---
title: "Where is the Money for Feminist Organizing? Survey for feminist, women’s rights and gender justice movements, groups and organizations"
date: "`r Sys.Date()`"
output: html_document
---

#WITM follow up

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)
library(xlsx)

rm(list = ls())

```


**Database upload**

```{r upload, echo=T, message=F, warning=F}

# OPEN CSV file
witm <- read.csv2("Data/WITM_csv_last.csv")

source(file="WITM_variables.R") 
```
___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Group information:**

Q2. Which of the following statements best describes your group, organization and/or movement?

```{r info, echo=F, message=F, warning=F}
q1<-base %>%
  group_by(q1_description) %>% 
  mutate(q1_description=forcats::fct_recode(as_factor(q1_description),
                                                     "We promote the rights of women or girls or trans or gender diverse people in all their intersecting identities and this is the 'primary focus of all our work'" = "primary_focus",
                                            "We promote the rights of women or girls or trans or gender diverse people with intersecting identities 'through specific project(s)', but not as the primary focus of our work" = "specific_projects",
                                            "Other" = "98")) %>%
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q1_description)) %>% 
  rename("Description"=q1_description)



knitr::kable(q1) %>% 
  kable_minimal()
```


```{r info_other, echo=F, message=F, warning=F}
#Other responses

q1_otro<-base %>%
  filter(q1_description==98) %>% 
  group_by(q1_description_group) %>% 
  summarise(n=n()) %>% 
  select("Other"=q1_description_group)

knitr::kable(q1_otro) %>% 
  kable_minimal()

```
**--Analysis notes-----------------------------------------------------------------------**



**------------------------------------------------------------------------------------------------**

___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Organization names:**

Q3. The name organizations that answered Q2-B (specific project)


```{r name, echo=F, message=F, warning=F}
q2<-base %>%
  filter(!is.na(q2_name) & !q1_description=='specific_projects') %>% 
  group_by(q2_name) %>% 
  select("Organization names"=q2_name) 
  
knitr::kable(q2) %>% 
  kable_minimal()

```

___


**q2 croostab with q4 grouped on AWID focus subjects**



```{r, echo=F, message=F, warning=F}


 # "Anti-caste"="q4_forms_organizing.anti_caste",
 #                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
 #                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
 #                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
 #                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
 #                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
 #                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
 #                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
 #                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"


## Anti-caste 
q1q2_anti_caste<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.anti_caste,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.anti_caste,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q1q2_peace<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.anti_militarization,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.anti_militarization,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q1q2_climate<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.climate_justice,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.climate_justice,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q1q2_anti_rights<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.countering_anti_gender,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.countering_anti_gender,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q1q2_care<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.holistic_safety_protection_collective_care,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q1q2_lesbian<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.lesbian_bisexual_queer_rights,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q1q2_sex_workers<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.sex_workers_rights,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.sex_workers_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q1q2_trans<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.trans_non_binary_rights,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.trans_non_binary_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q1q2_others<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_awid_focus_no,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_awid_focus_no,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )

q1q2_all<-bind_rows(q1q2_anti_caste,q1q2_peace,q1q2_climate,q1q2_anti_rights,q1q2_care,q1q2_lesbian,q1q2_sex_workers,q1q2_trans,q1q2_others)

q1q2_all <-q1q2_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q1_description,percentage)


qry_w<-q1q2_all %>% pivot_wider(names_from = q1_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```




**--Analysis notes-----------------------------------------------------------------------**

This crosstabulation shows the information upside down. It indicates that: among the organizations that indicated that they work on some of the main issues of the feminist agenda, 78.3% indicated that they work with a focus on that agenda and 15% through projects. The distribution is very stable among all the issues.


**------------------------------------------------------------------------------------------------**


```{r}
q2q4

qry_graph<-q2q4 %>% pivot_longer(cols=c("Specific feminist subjects","General HR Subjects","Intersectionality (minority groups)","Sexual and reproductive health & rights"), names_to = "q4_grouped", values_to = "percentage")

qry_graph<-qry_graph %>% filter(Description=="Primary focus" | Description=="Specific projects" )
qry_graph

ggplot(qry_graph, aes(x = q4_grouped, y=percentage, fill=Description)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller(palette = "Red-Green") +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Subjects grouped by type of organization (%)") +                
  theme_light()+
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=-0.2, size=3) 

```


**--Analysis notes-----------------------------------------------------------------------**
It reads as follows: Among the organizations that work on the basis of specific projects, 62.9% indicated working on some of the main themes of feminism, while 48.8% indicated working in relation to groups in situation of vulnerability. They may have chosen more than one option (they overlap).


**------------------------------------------------------------------------------------------------**


**Organisation type & subjetcs - grouped**

Option 2 

```{r q2_q4, echo=F, message=F, warning=F}




 #fem=sum(q4_grouped_feminist==1),
 #       hr=sum(q4_grouped_hr==1),
  #     min=sum(q4_grouped_minorities==1),
  #      srhr=sum(q4_grouped_srhr==1),
       

#q1_description

## FEMINIST FOCUS 
q1q2_feminist<-base %>%
  filter(!is.na(q1_description) & q1_description!="" & q4_grouped_feminist!="98") %>%
  group_by(q4_grouped_feminist,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_grouped_feminist,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Specific feminist subjects (A)","0"="Other subjects")
         )
##HR GENERAL SUBJECT 
q1q2_HR<-base %>%
  filter(!is.na(q1_description) & q1_description!="" & q4_grouped_hr!="98") %>%
  group_by(q4_grouped_hr,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_grouped_hr,percentage)%>%
   mutate(q4_grouped=recode(q4_grouped,"1"="HR general subjects (B)","0"="Other subjects")
         )  


##Intersectionality
q1q2_minorities<-base %>%
  filter(!is.na(q1_description) & q1_description!="" & q4_grouped_minorities!="98") %>%
  group_by(q4_grouped_minorities,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
   mutate(q4_grouped_minorities=recode(q4_grouped_minorities,"1"=" Intersectionality subjects (C) ","0"="Other subjects")
         )  %>%
  select(q1_description,q4_grouped=q4_grouped_minorities,percentage)


##Sexual and reproductive health & rights
q1q2_srhr<-base %>%
  filter(!is.na(q1_description) & q1_description!="" & q4_grouped_srhr!="98") %>%
  group_by(q4_grouped_srhr,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
   mutate(q4_grouped_srhr=recode(q4_grouped_srhr,"1"=" Sexual and reproductive health & rights (D) ","0"="Other subjects")
         )  %>%
  select(q1_description,q4_grouped=q4_grouped_srhr,percentage)

q1q2_all<-bind_rows(q1q2_feminist,q1q2_HR,q1q2_minorities,q1q2_srhr)

q1q2_all <-q1q2_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q1_description,percentage)


qry_w<-q1q2_all %>% pivot_wider(names_from = q4_grouped, values_from = percentage) %>%
 mutate(q1_description=recode(q1_description,  "98"="Other", "primary_focus"="Primary focus", "specific_projects"="Specific projects"))
         

knitr::kable(qry_w) %>% 
  kable_minimal()



```




**--Analysis notes-----------------------------------------------------------------------**

This crosstabulation shows the information upside down. It indicates that: among the organizations that indicated that they work on some of the main issues of the feminist agenda, 78.3% indicated that they work with a focus on that agenda and 15% through projects. The distribution is very stable among all the issues.


**------------------------------------------------------------------------------------------------**

___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Register**

Q5. Is your group, organization and/or movement registered?

```{r registered, echo=F, message=F, warning=F}

q5<-base %>%
  group_by(q5_registered) %>% 
  mutate(q5_registered= case_when(
    q5_registered=="y_registered" ~ "Yes",
    q5_registered=="n_registered" ~ "No",
    q5_registered==98 ~ "Other",
    TRUE ~ NA)) %>%  
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(n)) %>% 
  rename("Register"=q5_registered)

knitr::kable(q5) %>% 
  kable_minimal()

```

___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Register by type of organisation**

A crosstabulation (bivariate) of the combination of organization type and registration is shown.

```{r q5_q1, echo=F, message=F, warning=F}

q5q2<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="" & !is.na(q1_description)) %>%
  group_by(q1_description,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(Registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered")
         , q1_description=recode(q1_description,"98"="Other","primary_focus"="Primary focus","specific_projects"="Specific Projects")
         ) %>%
  select(q1_description,Registered,percentage)

qry_w<-q5q2 %>% pivot_wider(names_from = q1_description, values_from = percentage)

knitr::kable(qry_w) %>% 
  kable_minimal()


```


```{r}
#q5q2

  qry_graph<-q5q2 %>% filter((q1_description=="Primary focus" | q1_description=="Specific Projects") & (Registered=="Registered"  | Registered=="No registered"))
#qry_graph

ggplot(qry_graph, aes(x = q1_description, y=percentage, fill=Registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Type of organization by registration (%)") +                
  theme_light()+
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=-0.2, size=3) 

```

**--Analysis notes-----------------------------------------------------------------------**

The behavior between "primary focus" and "specific projects" organizations is similar in terms of registration. There are slightly more unregistered primary focus organizations, but this is not a relevant difference.

**------------------------------------------------------------------------------------------------**


___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Register by subject - grouped**
A crosstabulation (bivariate) of the combination of registration and subject of the organisation 


```{r q4xq5, echo=F, message=F, warning=F}

 #fem=sum(q4_grouped_feminist==1),
 #       hr=sum(q4_grouped_hr==1),
  #     min=sum(q4_grouped_minorities==1),
  #      srhr=sum(q4_grouped_srhr==1),
       


## FEMINIST FOCUS 
q5q2_feminist<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="" & q4_grouped_feminist!="98") %>%
  group_by(q4_grouped_feminist,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_grouped_feminist,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Specific feminist subjects (A)","0"="Other subjects")
         )
##HR GENERAL SUBJECT 
q5q2_HR<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="" & q4_grouped_hr!="98") %>%
  group_by(q4_grouped_hr,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_grouped_hr,percentage)%>%
   mutate(q4_grouped=recode(q4_grouped,"1"="HR general subjects (B)","0"="Other subjects")
         )  


##Intersectionality
q5q2_minorities<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="" & q4_grouped_minorities!="98") %>%
  group_by(q4_grouped_minorities,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
   mutate(q4_grouped_minorities=recode(q4_grouped_minorities,"1"=" Intersectionality subjects (C) ","0"="Other subjects")
         )  %>%
  select(q5_registered,q4_grouped=q4_grouped_minorities,percentage)


##Sexual and reproductive health & rights
q5q2_srhr<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="" & q4_grouped_srhr!="98") %>%
  group_by(q4_grouped_srhr,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
   mutate(q4_grouped_srhr=recode(q4_grouped_srhr,"1"=" Sexual and reproductive health & rights (D) ","0"="Other subjects")
         )  %>%
  select(q5_registered,q4_grouped=q4_grouped_srhr,percentage)

q5q2_all<-bind_rows(q5q2_feminist,q5q2_HR,q5q2_minorities,q5q2_srhr)

q5q2_all <-q5q2_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q5_registered,percentage)


qry_w<-q5q2_all %>% pivot_wider(names_from = q4_grouped, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))
         
knitr::kable(qry_w) %>% 
  kable_minimal()



```

**--Analysis notes-----------------------------------------------------------------------**

This cross-tabulation allows for comparison according to the issues they address and whether or not the organizations are registered. Reading: among those working mainly on specific feminist issues, 80% are registered, while among those working on general human rights issues, this value rises to 83%.


**------------------------------------------------------------------------------------------------**


___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope:**

Q6. What is the geographical scope of your work?

```{r scope, echo=F, message=F, warning=F}

q6<-base %>% 
  group_by(q6_geo_scope) %>% 
  mutate(q6_geo_scope=forcats::fct_recode(as_factor(q6_geo_scope),
                                                     "Locally" = "locally_focused",
                                            "Nationally" = "nationally_focused",
                                          "Work from diaspora, refuge and/or exile" = "diaspora_and_or_exile",
                                          "Regionally" = "regionally_focused",
                                          "Transnationally" = "transnationally_focused",
                                          "Global" = "globally_focused")) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(q6_geo_scope) %>% 
  rename("Geo scope"=q6_geo_scope)


knitr::kable(q6) %>% 
  kable_minimal()
```

**--Analysis notes-----------------------------------------------------------------------**
The sample is very interesting because most of the organizations are national or local (80%). 


**------------------------------------------------------------------------------------------------**
___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope by type of organisation**


A crosstabulation (bivariate) of the combination of type of organization type and scope

```{r q5_q2, echo=F, message=F, warning=F}

##borrar las variables para evitar problemas
#rm(list=setdiff(ls(), "base"))

q6q2<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="" & !is.na(q1_description)) %>%
  group_by(q6_geo_scope,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q6_geo_scope=recode(q6_geo_scope,
         "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"
         ) ) %>%
  select(q1_description,Scope=q6_geo_scope,percentage)


qry_w<-q6q2 %>% pivot_wider(names_from = Scope, values_from = percentage)


knitr::kable(qry_w) %>% 
  kable_minimal()


```

```{r}
q6q2

  qry_graph<-q6q2 %>% filter((q1_description=="primary_focus" | q1_description=="specific_projects") & (Scope=="Nationally"  | Scope=="Locally" | Scope=="Regionally"))
#qry_graph

ggplot(qry_graph, aes(x = Scope, y=percentage, fill=q1_description)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Type of organization by Geographic scope (%)") +                
  theme_light()+
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=-0.2, size=3) 

```

**--Analysis notes-----------------------------------------------------------------------**

So far, due to the size of the sample, it is only convenient to analyze this crossover for the 3 most numerous groups: national, local and regional. In these 3 cases, the distribution is homogeneous, and there is a slight tendency to work on feminism and gender issues through projects for regional organizations.

**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope by registration**


A crosstabulation (bivariate) of the combination of registered and scope

```{r q6_q2, echo=F, message=F, warning=F}

##borrar las variables para evitar problemas
rm(list=setdiff(ls(), "base"))

q5q2<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="" & !is.na(q5_registered)) %>%
  group_by(q6_geo_scope,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q6_geo_scope=recode(q6_geo_scope,
          "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"
         ) ) %>%
  select(q5_registered,Scope=q6_geo_scope,percentage)

#q5q2
qry_w<-q5q2 %>% pivot_wider(names_from = Scope, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))

knitr::kable(qry_w) %>% 
  kable_minimal()


```

```{r}
#q5q2

  qry_graph<-q5q2 %>% filter((q5_registered=="y_registered" | q5_registered=="n_registered") & (Scope=="Nationally"  | Scope=="Locally" | Scope=="Regionally"))
#qry_graph

ggplot(qry_graph, aes(x = Scope, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Registration by Geographic scope (%)") +                
  theme_light()+
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=-0.2, size=3) 

```
**--Analysis notes-----------------------------------------------------------------------**
The same analysis as before shows that there is a greater tendency for local organizations to be unregistered.

**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope & subjetcs - grouped**

Option 1

```{r}

scope_filter=c("locally_focused","nationally_focused","regionally_focused")

q6q4<-base %>%
  filter(!is.na(q6_geo_scope) & !is.na(q4_grouped_feminist) & (q6_geo_scope %in% scope_filter)) %>%
  group_by(q6_geo_scope) %>%
  summarise(total=n(),
        fem=sum(q4_grouped_feminist==1),
        hr=sum(q4_grouped_hr==1),
        min=sum(q4_grouped_minorities==1),
        srhr=sum(q4_grouped_srhr==1),
        'Specific feminist subjects'=round(fem/total*100,2),
        'General HR Subjects'=round(hr/total*100,2),
        'Intersectionality (minority groups)'=round(min/total*100,2),
        'Sexual and reproductive health & rights'=round(srhr/total*100,2)) %>%
  mutate(q6_geo_scope=recode(q6_geo_scope,
          "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"
         )) %>%
  select("Scope"="q6_geo_scope",7:10)  

q6q4

qry_w<-t(q6q4)
        

knitr::kable(qry_w) %>% 
  kable_minimal()
```

**--Analysis notes-----------------------------------------------------------------------**

Regional organizations work more often on specifically feminist issues than on group issues, at least in relation to local and national organizations.

**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope & subjetcs - grouped**

Option 2: how is distributed inside each subject the scope
Absolutes numbers


```{r q6_q4, echo=F, message=F, warning=F}


rm(list=setdiff(ls(), "base"))

 #fem=sum(q4_grouped_feminist==1),
 #       hr=sum(q4_grouped_hr==1),
  #     min=sum(q4_grouped_minorities==1),
  #      srhr=sum(q4_grouped_srhr==1),
       

#q1_description

## FEMINIST FOCUS 
q6q4_feminist<-base %>%
  filter(!is.na(q6_geo_scope)  & q4_grouped_feminist!="98") %>%
  group_by(q4_grouped_feminist,q6_geo_scope)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_grouped_feminist,n) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Specific feminist subjects (A)","0"="Other subjects")
         )

##HR GENERAL SUBJECT 
q6q4_HR<-base %>%
 filter(!is.na(q6_geo_scope)  & q4_grouped_hr!="98") %>%
  group_by(q4_grouped_hr,q6_geo_scope)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_grouped_hr,n)%>%
   mutate(q4_grouped=recode(q4_grouped,"1"="HR general subjects (B)","0"="Other subjects")
         )  


##Intersectionality
q6q4_minorities<-base %>%
   filter(!is.na(q6_geo_scope)  & q4_grouped_minorities!="98") %>%
  group_by(q4_grouped_minorities,q6_geo_scope)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
   mutate(q4_grouped_minorities=recode(q4_grouped_minorities,"1"=" Intersectionality subjects (C) ","0"="Other subjects")
         )  %>%
  select(q6_geo_scope,q4_grouped=q4_grouped_minorities,n)


##Sexual and reproductive health & rights
q6q4_srhr<-base %>%
   filter(!is.na(q6_geo_scope)  & q4_grouped_srhr!="98") %>%
  group_by(q4_grouped_srhr,q6_geo_scope)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
   mutate(q4_grouped_srhr=recode(q4_grouped_srhr,"1"=" Sexual and reproductive health & rights (D) ","0"="Other subjects")
         )  %>%
  select(q6_geo_scope,q4_grouped=q4_grouped_srhr,n)

q6q4_all<-bind_rows(q6q4_feminist,q6q4_HR,q6q4_minorities,q6q4_srhr)

q6q4_all <-q6q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q6_geo_scope,n)


qry_w<-q6q4_all %>% pivot_wider(names_from = q4_grouped, values_from = n) %>%
 mutate(q6_geo_scope=recode(q6_geo_scope,
          "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"))
         

knitr::kable(qry_w) %>% 
  kable_minimal()



```

**--Analysis notes-----------------------------------------------------------------------**

These data allow us to see how many organizations of each type indicated working on each of the topics. This crosswalk is useful during implementation, then it should be replaced by the percentage.

**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Region:**

Q7. Indicate in which region(s) your group, organization and/or movement works

*Reading: 22% of the organizations work in South Asia.
Organizations working locally, regionally or globally were consolidated.*


```{r region, echo=F, message=F, warning=F}



q7_a<-base %>% 
  filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one) %>%
    mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%   summarise(n=n())%>% 
  rename(q7=q7_region_one) %>% 
  arrange(q7)

q7_select<-base %>% 
  select(starts_with("q7_region_multiple.")) %>% 
  filter(!is.na(q7_region_multiple.samerica))


q7_b<-q7_select%>% 
  summarize_all(sum) %>% 
  gather(q7, n) %>% 
  mutate(q7= str_replace(q7, "q7_region_multiple.", "")) %>% 
  mutate(q7=forcats::fct_recode(as_factor(q7),
                                 "South America" = "samerica",
                                 "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica"))


q7_final <- q7_a %>% left_join(q7_b, by = "q7") %>% 
  mutate(n=n.x+n.y) %>% 
  select(-n.x,-n.y, "Region"=q7) %>%
  mutate(porcentaje=round((n/153)*100,1)) %>% 
  arrange(desc(porcentaje)) 
  
knitr::kable(q7_final) %>% 
  kable_minimal()

```

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Region by register**

This is made now only for Locally and National organisations

```{r region_q5, echo=F, message=F, warning=F}

rm(list=setdiff(ls(), "base"))

q5q7<-base %>% 
  filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one,q5_registered) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                    "South America" = "samerica",
                                    "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%
  select(q5_registered,Region=q7_region_one,percentage)

qry_w<-q5q7 %>% pivot_wider(names_from = Region, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))


knitr::kable(t(qry_w)) %>% 
  kable_minimal()

```

**--Analysis notes-----------------------------------------------------------------------**

Between local and national organizations there is a big difference in how many are unregistered in the different regions. The region with the highest proportion of unregistered is North Africa followed by North America.

**------------------------------------------------------------------------------------------------**

___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Country:**

Q8. Which countries are you working in?



```{r q6, recho=F, message=F, warning=F}

#Convertir campos vacíos de la variable country en NA
 base <- base %>%
  mutate(q8_country = na_if(q8_country, ""))

base<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%
  mutate(q8_country=forcats::fct_recode(as_factor(q8_country),
                                      "Afghanistan"="afghanistan",
                                      "Albania"="albania",
                                      "Algeria"="algeria",
                                      "American Samoa"="american_samoa",
                                      "Andorra"="andorra",
                                      "Angola"="angola",
                                      "Anguilla"="anguilla",
                                      "Antigua and Barbuda"="antigua_and_barbuda",
                                      "Argentina"="argentina",
                                      "Armenia"="armenia",
                                      "Aruba"="aruba",
                                      "Australia"="australia",
                                      "Austria"="austria",
                                      "Azerbaijan"="azerbaijan",
                                      "Bahamas"="bahamas",
                                      "Bahrain"="bahrain",
                                      "Bangladesh"="bangladesh",
                                      "Barbados"="barbados",
                                      "Belarus"="belarus",
                                      "Belgium"="belgium",
                                      "Belize"="belize",
                                      "Benin"="benin",
                                      "Bhutan"="bhutan",
                                      "Bolivia"="bolivia",
                                      "Bonaire, Sint Eustatius and Saba"="bonaire_sint_eustatius_saba",
                                      "Bosnia and Herzegovina"="bosnia_and_herzegovina",
                                      "Botswana"="botswana",
                                      "Brazil"="brazil",
                                      "British Virgin Islands"="british_virgin_islands",
                                      "Brunei Darussalam"="brunei_darussalam",
                                      "Bulgaria"="bulgaria",
                                      "Burkina Faso"="burkina_faso",
                                      "Burundi"="burundi",
                                      "Cabo Verde"="cabo_verde",
                                      "Cambodia"="cambodia",
                                      "Cameroon"="cameroon",
                                      "Canada"="canada",
                                      "Cayman Islands"="cayman_islands",
                                      "Central African Republic"="cafrican_republic",
                                      "Chad"="chad",
                                      "Chile"="chile",
                                      "China"="china",
                                      "Colombia"="colombia",
                                      "Comoros"="comoros",
                                      "Congo"="congo",
                                      "Cook Islands"="cook_islands",
                                      "Costa Rica"="costa_rica",
                                      "Côte d'Ivoire"="côte_divoire",
                                      "Croatia"="croatia",
                                      "Cuba"="cuba",
                                      "Curaçao"="curaçao",
                                      "Cyprus"="cyprus",
                                      "Czech Republic"="czech_republic",
                                      "Dem. People's Republic of Korea"="dem_peoples_rep_of_korea",
                                      "Democratic Republic of the Congo"="democratic_republic_of_the_congo",
                                      "Denmark"="denmark",
                                      "Djibouti"="djibouti",
                                      "Dominica"="dominica",
                                      "Dominican Republic"="dominican_republic",
                                      "Ecuador"="ecuador",
                                      "Egypt"="egypt",
                                      "El Salvador"="el_salvador",
                                      "Equatorial Guinea"="equatorial_guinea",
                                      "Eritrea"="eritrea",
                                      "Estonia"="estonia",
                                      "Eswatini"="eswatini",
                                      "Ethiopia"="ethiopia",
                                      "Fiji"="fiji",
                                      "Finland"="finland",
                                      "France"="france",
                                      "French Guiana"="french_guiana",
                                      "French Polynesia"="french_polynesia",
                                      "Gabon"="gabon",
                                      "Gambia"="gambia",
                                      "Georgia"="georgia",
                                      "Germany"="germany",
                                      "Ghana"="ghana",
                                      "Greece"="greece",
                                      "Greenland"="greenland",
                                      "Grenada"="grenada",
                                      "Guadeloupe"="guadeloupe",
                                      "Guam"="guam",
                                      "Guatemala"="guatemala",
                                      "Guinea"="guinea",
                                  "Guinea-Bissau"="guinea_bissau",
                                      "Guyana"="guyana",
                                      "Haiti"="haiti",
                                      "Honduras"="honduras",
                                      "Hong Kong"="hong_kong",
                                      "Hungary"="hungary",
                                      "Iceland"="iceland",
                                      "India"="india",
                                      "Indonesia"="indonesia",
                                      "Iran"="iran",
                                      "Iraq"="iraq",
                                      "Ireland"="ireland",
                                      "Israel"="israel",
                                      "Italy"="italy",
                                      "Jamaica"="jamaica",
                                      "Japan"="japan",
                                      "Jordan"="jordan",  
                                      "Kazakhstan"="kazakhstan",
                                  "Kenya"="kenya",
                                  "Kiribati"="kiribati",
                                  "Kuwait"="kuwait",
                                  "Kyrgyzstan"="kyrgyzstan",
                                  "Lao People's Democratic Republic"="lao_peoples_democratic_republic",
                                  "Latvia"="latvia",
                                  "Lebanon"="lebanon",
                                  "Lesotho"="lesotho",
                                  "Liberia"="liberia",
                                  "Libya"="libya",
                                  "Liechtenstein"="liechtenstein",
                                  "Lithuania"="lithuania",
                                  "Luxembourg"="luxembourg",
                                  "Macao"="macao",
                                  "Madagascar"="madagascar",
                                  "Malawi"="malawi",
                                  "Malaysia"="malaysia",
                                  "Maldives"="maldives",
                                  "Mali"="mali",
                                  "Malta"="malta",
                                  "Marshall
                                  Islands"="marshall_islands",
                                  "Martinique"="martinique",
                                  "Mauritania"="mauritania",
                                  "Mauritius"="mauritius",
                                  "Mayotte"="mayotte",
                                  "Mexico"="mexico",
                                  "Micronesia (Fed. States of)"="micronesia_fed_states_of",
                                  "Monaco"="monaco",
                                  "Mongolia"="mongolia",
                                  "Montenegro"="montenegro",
                                  "Montserrat"="montserrat",
                                  "Morocco"="morocco",
                                  "Mozambique"="mozambique",
                                  "Myanmar"="myanmar",
                                  "Namibia"="namibia",
                                  "Nauru"="nauru",
                                  "Nepal"="nepal",
                                  "Netherlands"="netherlands",
                                  "New Caledonia"="new_caledonia",
                                  "New Zealand"="new_zealand",
                                  "Nicaragua"="nicaragua",
                                  "Niger"="niger",
                                  "Nigeria"="nigeria",
                                "Niue"="niue",
                                "North Macedonia"="north_macedonia",
                                "Northern Mariana Islands"="northern_mariana_islands",
                                "Norway"="norway",
                                "Oman"="oman",
                                "Pakistan"="pakistan",
                                "Palau"="palau",
                                "Palestine"="palestine",
                                "Panama"="panama",
                                "Papua New Guinea"="papua_new_guinea",
                                "Paraguay"="paraguay",
                                "Peru"="peru",
                                "Philippines"="philippines",
                                "Poland"="poland",
                                "Portugal"="portugal",
                                "Puerto Rico"="puerto_rico",
                                "Qatar"="qatar",
                                "Republic of Korea"="republic_of_korea",
                                "Republic of Moldova"="republic_of_moldova",
                                "Réunion"="reunion",
                                "Romania"="romania",
                                "Russia"="russia",
                                "Rwanda"="rwanda",
                                "Saint Barthélemy"="saint_barthelemy",
                                "Saint Helena"="saint_helena",
                                "Saint Kitts and Nevis"="saint_kitts_and_nevis",
                                "Saint Lucia"="saint_lucia",
                                "Saint Martin (French part)"="saint_martin_french_part",
                                "Saint Vincent and the Grenadines"="saint_vincent_and_the_grenadines",
                                "Samoa"="samoa",
                                "San Marino"="san_marino",
                                "Sao Tome and Principe"="sao_tome_and_principe",
                                "Saudi Arabia"="saudi_arabia",
                                "Senegal"="senegal",
                                "Serbia"="serbia",
                                "Seychelles"="seychelles",
                                "Sierra Leone"="sierra_leone",
                                "Singapore"="singapore",
                                "Sint Maarten (Dutch part)"="sint_maarten_dutch_part",
                                "Slovakia"="slovakia",
                                "Slovenia"="slovenia",
                                "Solomon Islands"="solomon_islands",
                                "Somalia"="somalia",
                                "South Africa"="south_africa",
                                "South Sudan"="south_sudan",
                                "Spain"="spain",
                                "Sri Lanka"="sri_lanka",
                                "Sudan"="sudan",
                                "Suriname"="suriname",
                                "Sweden"="sweden",
                                "Switzerland"="switzerland",
                                "Syrian Arab Republic"="syrian_arab_republic",
                                "Taiwan"="taiwan",
                                "Tajikistan"="tajikistan",
                                "Tanzania"="tanzania",
                                "Thailand"="thailand",
                                "Timor-Leste"="timor_leste",
                                "Togo"="togo",
                                "Tokelau"="tokelau",
                                "Tonga"="tonga",
                                "Trinidad and Tobago"="trinidad_and_tobago",
                                "Tunisia"="tunisia",
                                "Turkey"="turkey",
                                "Turkmenistan"="turkmenistan",
                                "Turks and Caicos Islands"="turks_and_caicos_islands",
                                "Tuvalu"="tuvalu",
                                "Uganda"="uganda",
                                "Ukraine"="ukraine",
                                "United Arab Emirates"="united_arab_emirates",
                                "United Kingdom"="united_kingdom",
                                "United States of America"="united_states_of_america",
                                "Uruguay"="uruguay",
                                "Uzbekistan"="uzbekistan",
                                "Vanuatu"="vanuatu",
                                "Venezuela (Bolivarian Republic of)"="venezuela_bolivarian_republic_of",
                                "Viet Nam"="viet_nam",
                                "Wallis and Futuna Islands"="wallis_and_futuna_islands",
                                "Western Sahara"="western_sahara",
                                "Yemen"="yemen",
                                "Zambia"="zambia",
                                "Zimbabwe"="zimbabwe",
                                "Other South America"="country_other1",
                                "Other Central America & Mexico"="country_other2",
                                "Other North America"="country_other3",
                                "Other Caribbean"="country_other4",
                                "Other South Asia"="country_other5",
                                "Other Southeast Asia"="country_other6",
                                "Other East Asia"="country_other7",
                                "Other The Pacific"="country_other8",
                                "Other South West Asia/Middle East"="country_other9",
                                "Other Central Asia & Caucasus"="country_other10",
                                "Other Eastern Europe, Southeast Europe and Central Europe"="country_other11",
                                "Other Western Europe"="country_other13",

                              "Other West Africa"="country_other14",
                              "Other East Africa"="country_other15",
                              "Other Southern Africa"="country_other16",
                              "Other Central Africa"="country_other17",
                              "Other North Africa"="country_other18"))


q8<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one, q8_country) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1))

knitr::kable(q8) %>% 
  kable_minimal()

```

**--Analysis notes-----------------------------------------------------------------------**

This is the detailed list that allows you to see in which countries the answers were obtained, not those that did not have a response

**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year of formation:**

Q9. What year was your group, organization and/ or movement formed?

*Reading: 36% of the respondent organizations were formed between the years 2015 and 2020, while around 13% were formed from the year 2021 onwards*


```{r year, echo=F, message=F, warning=F}


    

q9<-base %>% 
  filter(!is.na(q9_year_formation_agrup)) %>% 
  group_by(q9_year_formation_agrup) %>% 
  summarise(total=n()) %>% 
  mutate(porcentaje=round((total/sum(total))*100,1)) %>% 
  arrange(q9_year_formation_agrup) %>% 
  rename("Year formation"=q9_year_formation_agrup)


knitr::kable(q9) %>% 
  kable_minimal()


```

___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year of formation & Register**



```{r year_register, echo=F, message=F, warning=F}



q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup)) %>% 
  group_by(q9_year_formation_agrup,q5_registered) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  select(q9_year_formation_agrup,q5_registered,percentage)


qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))


knitr::kable(qry_w) %>% 
  kable_minimal()



```


```{r}
#q8

  qry_graph<-q8 %>% filter((q5_registered=="y_registered" | q5_registered=="n_registered"))
#qry_graph

ggplot(qry_graph, aes(x = q9_year_formation_agrup, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Year",y= "%") +                 
  ggtitle("Year of statup by Registration (%)") +                
  theme_light()+
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=-0.2, size=3) 

```


**--Analysis notes-----------------------------------------------------------------------**

Organizations starting in the last 3 years have a high proportion of non-registration. It decreases as the start-up time passes.


**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year by type of organisation**


```{r year_q9, echo=F, message=F, warning=F}

q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup) & !is.na(q1_description)) %>% 
  group_by(q9_year_formation_agrup,q1_description) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  select(q9_year_formation_agrup,q1_description,percentage)

qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage)%>%
 mutate(q1_description=recode(q1_description,"98"="Other","primary_focus"="Primary focus","specific_projects"="Specific Projects")
 )


knitr::kable(qry_w) %>% 
  kable_minimal()



```


**--Analysis notes-----------------------------------------------------------------------**

Organizations starting in the last 3 years have a high proportion of non-registration. It decreases as the start-up time passes.


**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year by Gegraphically Scope**

Option 1

```{r year_q6, echo=F, message=F, warning=F}

#rm(list=setdiff(ls(), "base"))

qry<-base %>%
    group_by(q6_geo_scope) %>%
  summarise(n=n())

qry

q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup) & !is.na(q6_geo_scope)) %>% 
  group_by(q9_year_formation_agrup,q6_geo_scope) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  mutate(q6_geo_scope=recode(q6_geo_scope,
     "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
         "transnationally_focused"="Transnationally",
         "globally_focused"="Global")) %>%
  select(q9_year_formation_agrup,q6_geo_scope,percentage)


qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage)
       
 


knitr::kable(qry_w) %>% 
  kable_minimal()



```

```{r}
#rm(list=setdiff(ls(), "base"))

scope_filter=c("Locally","Nationally","Regionally","Global")

q8 <- q8 %>% filter(q6_geo_scope %in% scope_filter)

ggplot(q8, aes(x = q9_year_formation_agrup, y=percentage, fill=q6_geo_scope)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_fill_brewer(palette = "Set3") +
  labs(x="Year",y= "%") +                 
  ggtitle("Geographical scope by year(%)") +                
  theme_bw(base_size = 12)+
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=-0.2, size=3) 
  

```


**--Analysis notes-----------------------------------------------------------------------**

The distribution is quite similar in all periods.


**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**
SECTION : EXTERNAL FOUNDING
**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**External founding:**

Q13. Between 2021 and 2023, has your group, organization and/or movement received any external funding?


```{r ef, echo=F, message=F, warning=F}
q13<-base %>%
  group_by(q13_ext_funding) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  rename("External funding"=q13_ext_funding)
 

knitr::kable(q13) %>% 
  kable_minimal()
```
___



