---
title: "WITM-Analisys Q2"
date: "`r Sys.Date()`"
output: html_document
---

#WITM Q2 analysis

*Q2. Which of the following statements best describes your group, organization and/or movement?
Hint: by “intersecting identities,” we refer to multiple and overlapping factors, including but not limited to gender identity, race, ethnicity, class, migration status, religious beliefs, sexual expression and identity, etc.


a)	We promote the rights of women or girls or trans or gender diverse people with intersecting identities, and this is the “primary focus of all our work”.

b)	We promote the rights of women or girls or trans or gender diverse people with intersecting identities “through specific project(s)”, but not as the primary focus of our work.

c) Other (please briefly share to what extent the rights of women, girls, trans or gender diverse people are a priority for your work)



```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)


rm(list = ls())
```



```{r upload, echo=F, message=F, warning=F}

# OPEN CSV file

witm <- read.csv("Data/WITM_cleaned_20240912.csv")

##source(file="WITM_variables.R") 

```
___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Group information:**

Q2. Which of the following statements best describes your group, organization and/or movement?

```{r info, echo=F, message=F, warning=F}
q2<-witm %>%
  group_by(q2_description) %>% 
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a) Feministe organizations (primary focus)" = "primary_focus",
                                            "b) Organizations that promote the rights of women or girls through specific project(s) (specific_projects)" = "specific_projects",
                                            "c) Other" = "98")) %>%
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  rename("Description"=q2_description) %>% 
  arrange(desc(porcentaje)) 



knitr::kable(q2) %>% 
  kable_minimal()
```


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-

Most of the organizations are feminist (primary focus). The 7% can be reduced by cleaning and some can also be reassigned from group b) to a).


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


**q2 croostab with q4 grouped on AWID Spotlight themes/groups**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q4_forms_organizing) & q4_forms_organizing!="98") %>%
  group_by(q2_description,q4_awid_focus)%>%
  mutate(q4_awid_focus=forcats::fct_recode(as_factor(q4_awid_focus),
                                                     "Spotlight" = "1",
                                            "Other subjects" = "0")) %>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus"  = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  arrange(q2_description)

#qry

qry_w<-qry %>% select (q4_awid_focus,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```


```{r, echo=F, message=F, warning=F}

ggplot(qry, aes(x = q2_description, y=percentage, fill=q4_awid_focus)) +                      
   geom_bar(position="dodge", stat="identity") +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Q2 by Q4-grouped") +                
  theme_minimal() +
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) 

```



-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-

The data show that primary focus organizations work proportionally more on AWID's priority issues than "per project" organizations. Even so, the difference (81.5 vs. 76.4) is not very significant (around 5%).

-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


**q2 croostab with q5 registration**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q5_registered) & q5_registered!="98") %>%
  group_by(q2_description,q5_registered)%>%
   mutate(q5_registered= case_when(
    q5_registered=="y_registered" ~ "Yes",
    q5_registered=="n_registered" ~ "No",
    q5_registered==98 ~ "Other",
    TRUE ~ NA)) %>%  
   mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q5_registered,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```



```{r}

ggplot(qry, aes(x = q2_description, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Q2",y= "%") +                 
  ggtitle("Q2 by Registration (%)") +                
  theme_light()+
 geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) 

```


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-

There is no significant difference in registration between Primary focus organizations and project organizations.


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-



**q2 croostab with q6 Scope**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98") %>%
  group_by(q2_description,q6_geo_scope)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q6_geo_scope,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


There is also no difference in how the geographic scope is distributed between the two types of organizations. If they were very different types of organizations, one would have expected the project organizations to be more global or regional, but this is not observed in the data.


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-

**q2 by year of formation**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q9_year_formation_agrup)) %>%
  group_by(q2_description,q9_year_formation_agrup)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q9_year_formation_agrup,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```




-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


There is also no difference in how the geographic scope is distributed between the two types of organizations. If they were very different types of organizations, one would have expected the project organizations to be more global or regional, but this is not observed in the data.


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-




**q2 by budget**

Only the year 2023 is taken as a reference for the analysis.


```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q10_budget_grp_2021)) %>%
  group_by(q2_description,q10_budget_grp_2021)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q10_budget_grp_2021,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```



-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


In relation to the budget, as can be seen, the distribution of the budget ranges are similar between the primary focus group and specific projects, especially the most important was to analyze the extremes (zero budgeted) and the highest ranges. In neither of these groups is there any distinctive trend between the two groups.


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-



**Q2 by Q13 external funding**  


```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q13_ext_funding)) %>%
  group_by(q2_description,q13_ext_funding)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q13_ext_funding,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


This is the first variable that shows a more significant difference, but with the opposite result to the expected: organizations working on a project basis are less likely to rely on external funding (64%) than targeted organizations (72.9).

-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


```{r, echo=F, message=F, warning=F}

#Convertir campos vacíos de la variable q15 en NA
 base <- witm %>%
  mutate(q15_key_sources = na_if(q15_key_sources, ""))

#Total valid responses for calculating Percentage

total<-witm %>%
  count(q15_key_sources) %>% 
  summarise(sum(n))

total<-total$n

q15 <- witm %>%
  filter( !is.na(q15_key_sources)) %>%
  group_by(q2_description)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  summarise(Total = n(),
    multirateral = sum(q15_key_sources.multilateral_funders == 1),
    bilateral = sum(q15_key_sources.bilateral_funders == 1),
    philanthropic = sum(q15_key_sources.philanthropic_foundations == 1),
    womens = sum(q15_key_sources.womens_feminist_funds == 1),
    private = sum(q15_key_sources.private_sector == 1),
    ingos = sum(q15_key_sources.ingos == 1),
    individual = sum(q15_key_sources.individual_donors == 1),
    gov = sum(q15_key_sources.national_local_goverment_or_bodies == 1),
    other = sum(q15_key_sources.98 == 1),
    Multirateral = round(multirateral / Total*100, 1),
    Bilateral = round(bilateral / Total*100, 1),
    Philanthropic = round(philanthropic / Total*100, 1),
    Feminist = round(womens / Total*100, 1),
    Private = round(private / Total*100, 1),
    INGOS = round(ingos / Total*100, 1),
    Individual = round(individual / Total*100, 1),
    Government = round(gov / Total*100, 1),
    Other = round(other / Total*100, 1)) %>% 
    select("Description"="q2_description",12:20) 

q15=t(q15)

knitr::kable(q15) %>% 
  kable_minimal()


```




-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


Regarding the sources of funding, there are some differences: primary focus organizations have a higher proportion of feminist funding (58.6% vs. 47.7%) and less funding from governments (15 vs. 20).

The overall distribution is however similar.

-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-

**Q2 by Q21**


**core funding**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q21_types_funding_2023_core)) %>%
   mutate(q21_core_2023=case_when(
   q21_types_funding_2023_core<26 ~"1 Up to 25%",
    q21_types_funding_2023_core>25 & q21_types_funding_2023_core<51 ~ "2 Between 26%-50%",
    q21_types_funding_2023_core>50 & q21_types_funding_2023_core<76 ~ "3 Between 51%-75%",
    is.na(q21_types_funding_2023_core) ~ NA,
    TRUE ~ "4 Over 75%")) %>% 
  group_by(q2_description,q21_core_2023)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q21_core_2023,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```


**Proyect funding**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q21_types_funding_2023_project)) %>%
   mutate(q21_project_2023=case_when(
   q21_types_funding_2023_project<26 ~"1 Up to 25%",
    q21_types_funding_2023_project>25 & q21_types_funding_2023_project<51 ~ "2 Between 26%-50%",
    q21_types_funding_2023_project>50 & q21_types_funding_2023_project<76 ~ "3 Between 51%-75%",
    is.na(q21_types_funding_2023_project) ~ NA,
    TRUE ~ "4 Over 75%")) %>% 
  group_by(q2_description,q21_project_2023)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q21_project_2023,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```

**Emergency funding**

```{r, echo=F, message=F, warning=F}

#q2xq4

qry<-witm %>%
  filter(!is.na(q21_types_funding_2023_emergency)) %>%
   mutate(q21_emergency_2023=case_when(
   q21_types_funding_2023_emergency<26 ~"1 Up to 25%",
    q21_types_funding_2023_emergency>25 & q21_types_funding_2023_emergency<51 ~ "2 Between 26%-50%",
    q21_types_funding_2023_emergency>50 & q21_types_funding_2023_emergency<76 ~ "3 Between 51%-75%",
    is.na(q21_types_funding_2023_project) ~ NA,
    TRUE ~ "4 Over 75%")) %>% 
  group_by(q2_description,q21_emergency_2023)%>%
  mutate(q2_description=forcats::fct_recode(as_factor(q2_description),
                                                     "a. Primary focus" = "primary_focus",
                                            "b. Specific project(s)" = "specific_projects",
                                            "c. Other" = "98")) %>%
  
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) 

#qry

qry_w<-qry %>% select (q21_emergency_2023,q2_description,percentage) %>% pivot_wider(names_from = q2_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()


```



-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


In relation to the types of funding (core, project and emergency) there are some minor differences. The main difference is seen in the proportion of core funding that the organizations have: 59.8% of the primary focus organizations have less than 25% of external funding of this type while this is the case for 68.9% of the organizations that work by project. That is, feminist organizations seem to have a higher proportion of core funding than the others.

-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-

-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-
-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-


**CONCLUSION**

Only 23% are organizations that declared themselves NOT FEMINIST but work by project on gender and diversity issues.

The latter (by project) work less frequently on AWID's priority issues (5% difference less, very little) and are registered in the same proportion as feminists (focus).

The geographical scope is also equivalent, for example, some are not more global and others more local, and they behave in the same way in relation to the year of training.

Up to this point, there are NO significant differences in any aspect.

Moving on to the analysis in relation to budget and funding, there are also minor differences in relation to budget, with only a slight tendency that project-based organizations seem to have lower budgets than feminist ones (slightly).

The only variable that shows a moderately significant difference is the existence or not of external funding: t basis are less likely to rely on external funding (64%) than targeted organizations (72.9).

Along the same lines, another slightly different variable indicates that feminist organizations have a higher proportion of core funding than those working on a project basis.


-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-
-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-
