---
title: "WITM 2024"
date: "`r Sys.Date()`"
output: html_document
---

#WITM Q4 ANALYSIS

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)
library(xlsx)

rm(list = ls())

```


## This reports aims to define a gruped q4 question for analysis




```{r upload, echo=T, message=F, warning=F}

# OPEN CSV file
witm <- read.csv2("Data/WITM_csv_last.csv")

source(file="WITM_variables.R") 
```
___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**


**Type of organization**

Q4. Which of the following forms of organizing best describes your group, organization and/or movement?

*This is a multiple-choice question so the sum of the % does NOT add up to 100.*

Original distribution

```{r}
##borrar las variables para evitar problemas
#
rm(list=setdiff(ls(), "base"))


#Total valid responses for calculating percentage

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(starts_with("q4_forms_organizing."))
#q4_select

#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Black rights/ Black feminist rights"="q4_forms_organizing.black_rights",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Crisis response"="q4_forms_organizing.crisis_response",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                "Digital rights"="q4_forms_organizing.digital_rights",
                                "Disability rights and justice"="q4_forms_organizing.disability_rights",
                                "Displaced, migrant and refugee rights"="q4_forms_organizing.displaced_migrant_refugee_rights",
                                "Economic justice, rights and alternatives"="q4_forms_organizing.economic_justice",
                                "Freedom of information and media"="q4_forms_organizing.information_media_freedom",
                                "Harm reduction"="q4_forms_organizing.harm_reduction",
                                "Ending gender based violence"="q4_forms_organizing.end_gender_violence",
                                "Pleasure and bodily care"="q4_forms_organizing.pleasure_bodily_care",
                                "Resisting the war on drugs"="q4_forms_organizing.resisting_war_on_drugs",
                                "Rights for people living with HIV+"="q4_forms_organizing.rights_for_people_living_with_hiv",
                                "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Human rights"="q4_forms_organizing.human_rights",
                                "Indigenous rights"="q4_forms_organizing.indigenous_rights",
                                "Intersex rights"="q4_forms_organizing.intersex_rights",
                                "Labour rights"="q4_forms_organizing.labour_rights",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Racial justice"="q4_forms_organizing.racial_justice",
                                "Religious and ethnic minority rights"="q4_forms_organizing.religious_ethnic_minority_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Sexual and reproductive health & rights (SRHR) and bodily autonomy"="q4_forms_organizing.srhr_bodily_autonomy",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Women's rights"="q4_forms_organizing.womens_rights",
                                "Young feminists"="q4_forms_organizing.young_feminists",
                                "Girls’ movements"="q4_forms_organizing.girls_movements",
                                "Human rights defenders at risk"="q4_forms_organizing.hr_defenders_at_risk",
                                "Other"="q4_forms_organizing.98"))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization type"=q4)

#write.xlsx2(as.data.frame(q4), "Output/section1.xlsx", row.names = FALSE, sheetName ="q4",append = TRUE)




knitr::kable(q4) %>% 
  kable_minimal()

```

```{r}
#names(base)

base<- base %>%
  mutate(q4_primary_categories=case_when(
          (q4_forms_organizing.womens_rights==1 |
          q4_forms_organizing.human_rights==1)  ~ 'HR or Women Rigts', TRUE ~ 'Other')) 
          
#Choose only multiple-choice answers -Q4-
q4_check<-base %>% 
  group_by(q4_primary_categories) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))
  

print(paste("The % of organizations that answer HR or Women rights is :",q4_check[1,3]))
#print('Maybe we need to not have this options inside the categories')

```

**GROUPED VARIABLE** 

A.	Organizing traditionally associated with feminism and women’s rights 

a.	Women’s rights
b.	Ending gender-based violence
c.	Sexual and reproductive health & rights (SRHR) and bodily autonomy
d.	Human rights

B.	Groups historically marginalized and invisibilized (in the funding ecosystem) 

a.	Young feminists
b.	Girls’ movements 
c.	Disability rights and justice
d.	Lesbian, bisexual and queer rights 
e.	Sex workers rights
f.	Rights for people living with HIV
g.	Displaced, migrants & refugee rights
h.	Indigenous rights
i.	Trans and non-binary-rights
j.	Labor rights (workers as a group)
k.	Intersex rights
l.	Black rights/feminist rights
m.	Anti-caste (small number of responses but relevant to AWID)
n.	Religious and ethnic minority rights
o.	Human rights defenders at risk

C.	By organizing focus – (others)

-	Climate and environmental justice – AWID FOCUS 
-	Countering anti-gender and anti-rights – AWID FOCUS
-	Anti-militarization and peace – AWID FOCUS
-	Holistic safety, protection and collective care – AWID FOCUS 
-	Resisting the war on drugs  
-	Economic justice, rights and alternatives
-	Crisis response
-	Digital rights
-	Racial justice 
-	Freedom of information and media
-	Harm reduction
-	Pleasure and bodily care




```{r}
#names(base)


base<- base %>%
  mutate(q4_grouped_feminist=case_when
         (
           (q4_forms_organizing.womens_rights==1 |
            q4_forms_organizing.human_rights==1  |
            q4_forms_organizing.end_gender_violence ==1  |
            q4_forms_organizing.srhr_bodily_autonomy==1) ~1, TRUE ~0)) %>%  
  
    mutate(q4_grouped_minorities=case_when
         (
           (
             q4_forms_organizing.young_feminists==1 |
             q4_forms_organizing.girls_movements ==1 |
             q4_forms_organizing.disability_rights==1 |
             q4_forms_organizing.lesbian_bisexual_queer_rights==1 |
             q4_forms_organizing.sex_workers_rights==1 |
             q4_forms_organizing.rights_for_people_living_with_hiv==1 |
             q4_forms_organizing.displaced_migrant_refugee_rights==1 |
             q4_forms_organizing.trans_non_binary_rights==1 |
             q4_forms_organizing.intersex_rights==1 |
             q4_forms_organizing.labour_rights==1 |
             q4_forms_organizing.indigenous_rights==1 |
             q4_forms_organizing.black_rights==1 |
             q4_forms_organizing.anti_caste==1 |
             q4_forms_organizing.hr_defenders_at_risk==1 |
             q4_forms_organizing.religious_ethnic_minority_rights==1 ) ~1, TRUE ~0)) %>% 
  
         
  mutate(q4_grouped_focus=case_when
         (
           (
              q4_forms_organizing.climate_justice==1 |
              q4_forms_organizing.countering_anti_gender==1 |
              q4_forms_organizing.anti_militarization==1 |
              q4_forms_organizing.holistic_safety_protection_collective_care==1 |
              q4_forms_organizing.resisting_war_on_drugs==1 |
              q4_forms_organizing.economic_justice==1 |
              q4_forms_organizing.crisis_response==1 |
              q4_forms_organizing.digital_rights==1 |
              q4_forms_organizing.racial_justice==1 |
              q4_forms_organizing.information_media_freedom==1 |
              q4_forms_organizing.harm_reduction==1 |
              q4_forms_organizing.pleasure_bodily_care==1) ~1, TRUE ~0)) 
 
  


```




```{r}


#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(starts_with("q4_grouped"))
#q4_select


#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "A.	Organizing traditionally associated with feminism and women’s rights  "="q4_grouped_feminist",
                                "B.	Groups historically marginalized and invisibilized"="q4_grouped_minorities",
                                "C.	By organizing focus – (others)"="q4_grouped_focus"
                                ))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization grouped type"=q4)

#write.xlsx2(as.data.frame(q4), "Output/section1.xlsx", row.names = FALSE, sheetName ="q4",append = TRUE)




knitr::kable(q4) %>% 
  kable_minimal()

```
___


**--Analysis notes-----------------------------------------------------------------------**


This classification does not really discriminate at all, i.e. all organizations chose between these groups.

For now it is recommended NOT to use this variable for any crossover.


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**



**Organisation type - FOCUS AWID**


VARIABLE THAT INDICATES IF THE ORGANIZATION WORKS OR NOT IN ONE OF THIS SUBJECTS


-	Lesbian, bisexual and queer rights 
-	Sex workers rights
-	Trans and non-binary-rights
-	Anti-caste 
-	Climate and environmental justice – AWID FOCUS 
-	Countering anti-gender and anti-rights – AWID FOCUS
-	Anti-militarization and peace – AWID FOCUS
-	Holistic safety, protection and collective care – AWID FOCUS




```{r}
#names(base)

#lo pase a variables
# base<- base %>%
#   mutate(q4_awid_focus=case_when
#          (
#            (q4_forms_organizing.lesbian_bisexual_queer_rights==1 |
#             q4_forms_organizing.sex_workers_rights==1  |
#             q4_forms_organizing.trans_non_binary_rights==1 |
#             q4_forms_organizing.anti_caste==1 |
#             q4_forms_organizing.climate_justice==1 |
#             q4_forms_organizing.countering_anti_gender==1 |
#             q4_forms_organizing.anti_militarization==1 |
#             q4_forms_organizing.holistic_safety_protection_collective_care==1) ~1, TRUE ~0))  
  

q4_focus<-base %>%
  filter( q4_grouped_feminist!="98") %>%
  group_by(q4_awid_focus) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  mutate(q4_awid_focus=recode(q4_awid_focus,"1"="Specific AWID subjects","0"="Other subjects")
         )


knitr::kable(q4_focus) %>% 
  kable_minimal()
  
  
```



**--Analysis notes-----------------------------------------------------------------------**

This classification is more interesting, it is impressive how many organizations are working on these issues.

**--------------------------------------------------------------------------------------**



**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Organisation type - FOCUS AWID - DETAIL**


Detail of q4 focus and the proportion of each of the topics in the total number of organizations working on one of AWID's priority topics.



```{r}


total_f<-base %>%
  filter(q4_awid_focus==1) %>%
  count(q4_awid_focus)
total_focus<-total_f$n


#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(q4_awid_focus,
         q4_forms_organizing.lesbian_bisexual_queer_rights,
            q4_forms_organizing.sex_workers_rights,
            q4_forms_organizing.trans_non_binary_rights,
            q4_forms_organizing.anti_caste,
            q4_forms_organizing.climate_justice,
            q4_forms_organizing.countering_anti_gender,
            q4_forms_organizing.anti_militarization,
            q4_forms_organizing.holistic_safety_protection_collective_care
         )
#q4_select


#q4 calculation
q4<-q4_select%>% 
  filter(q4_awid_focus==1) %>%
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Total focus organizations"="q4_awid_focus",
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights"
                   ))%>% 
  mutate(porcentaje=round(n/total_focus*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization type"=q4)


knitr::kable(q4) %>% 
  kable_minimal()

```

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**


## Organisation type - grouped - PROPOSAL


**To have the complete set, you can analyze the organizations according to which ones are in the Awid topics with this final distribution**



```{r}

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n

#lo pase a variables
# base<- base %>%
#   mutate(q4_awid_focus_no=case_when
#          (q4_awid_focus!=1 ~ 1, TRUE ~0))  
  

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(q4_forms_organizing.lesbian_bisexual_queer_rights,
            q4_forms_organizing.sex_workers_rights,
            q4_forms_organizing.trans_non_binary_rights,
            q4_forms_organizing.anti_caste,
            q4_forms_organizing.climate_justice,
            q4_forms_organizing.countering_anti_gender,
            q4_forms_organizing.anti_militarization,
            q4_forms_organizing.holistic_safety_protection_collective_care,
            q4_awid_focus_no
         )
#q4_select


#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"
                   ))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization type"=q4)


knitr::kable(q4) %>% 
  kable_minimal()




```



**AWID FOCUS SUBJECTS BY TYPE OF ORGANISATION**



```{r}


 # "Anti-caste"="q4_forms_organizing.anti_caste",
 #                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
 #                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
 #                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
 #                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
 #                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
 #                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
 #                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
 #                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"


## Anti-caste 
q1q2_anti_caste<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.anti_caste,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.anti_caste,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q1q2_peace<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.anti_militarization,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.anti_militarization,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q1q2_climate<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.climate_justice,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.climate_justice,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q1q2_anti_rights<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.countering_anti_gender,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.countering_anti_gender,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q1q2_care<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.holistic_safety_protection_collective_care,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q1q2_lesbian<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.lesbian_bisexual_queer_rights,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q1q2_sex_workers<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.sex_workers_rights,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.sex_workers_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q1q2_trans<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_forms_organizing.trans_non_binary_rights,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_forms_organizing.trans_non_binary_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q1q2_others<-base %>%
  filter(!is.na(q1_description) & q1_description!="98") %>%
  group_by(q4_awid_focus_no,q1_description)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q1_description,q4_grouped=q4_awid_focus_no,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )

q1q2_all<-bind_rows(q1q2_anti_caste,q1q2_peace,q1q2_climate,q1q2_anti_rights,q1q2_care,q1q2_lesbian,q1q2_sex_workers,q1q2_trans,q1q2_others)

q1q2_all <-q1q2_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q1_description,percentage)


qry_w<-q1q2_all %>% pivot_wider(names_from = q1_description, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```




**--Analysis notes-----------------------------------------------------------------------**

This is more relevant to the analysis of question q2 (see that report).


**------------------------------------------------------------------------------------------------**




**AWID FOCUS SUBJECTS BY REGISTRATION**


A crosstabulation (bivariate) of the combination of registration and subject of the organisation 


```{r}


 # "Anti-caste"="q4_forms_organizing.anti_caste",
 #                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
 #                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
 #                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
 #                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
 #                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
 #                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
 #                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
 #                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"


## Anti-caste 
q5q4_anti_caste<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.anti_caste,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.anti_caste,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q5q4_peace<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.anti_militarization,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.anti_militarization,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q5q4_climate<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.climate_justice,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.climate_justice,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q5q4_anti_rights<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.countering_anti_gender,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.countering_anti_gender,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q5q4_care<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.holistic_safety_protection_collective_care,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q5q4_lesbian<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.lesbian_bisexual_queer_rights,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q5q4_sex_workers<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.sex_workers_rights,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.sex_workers_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q5q4_trans<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.trans_non_binary_rights,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.trans_non_binary_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q5q4_others<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_awid_focus_no,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_awid_focus_no,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )

q5q4_all<-bind_rows(q5q4_anti_caste,q5q4_peace,q5q4_climate,q5q4_anti_rights,q5q4_care,q5q4_lesbian,q5q4_sex_workers,q5q4_trans,q5q4_others)

q5q4_all <-q5q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q5_registered,percentage)

q5q4_all
qry_w<-q5q4_all %>% pivot_wider(names_from = q5_registered, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```



**--Analysis notes-----------------------------------------------------------------------**

Anti-caste organizations are the most frequently unregistered. These data should be taken with caution, as this is the group with the fewest cases.


Those working on trans and non-binary rights also have a higher proportion of non-registrations than the others.

**------------------------------------------------------------------------------------------------**



___



