---
title: "WITM"
date: "`r Sys.Date()`"
output: html_document
---

#ANALYSIS - SECTION 2 

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)
library(xlsx)

rm(list = ls())

```


```{r upload, echo=T, message=F, warning=F}

# OPEN CSV file
witm <- read.csv2("Data/WITM_csv_last.csv")

source(file="WITM_variables.R") 

print(date())
```
___


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**
Section 2: Financial Status

Q10. What was the annual budget for your group, organization and/or movement in each of the following years in $USD?


```{r q10, echo=F, message=F, warning=F}
#Convertir campos vacíos de la variable q10 en NA
base <- base %>%
  mutate(q10_budget_year_2021 = na_if(q10_budget_year_2021, ""))

base <- base %>%
  mutate(q10_budget_year_2022 = na_if(q10_budget_year_2022, ""))
 
  base <- base %>%
  mutate(q10_budget_year_2023 = na_if(q10_budget_year_2023, ""))
 
#Organizaciones fondos anuales

q10_2021<-base %>% 
  filter(q9_year_formation<2022) %>% 
  group_by(q10_budget_year_2021) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  rename("Annual_budget"=q10_budget_year_2021) %>% 
  mutate(Year=2021)

q10_2022<-base %>% 
  filter(q9_year_formation<2023) %>% 
  group_by(q10_budget_year_2022) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  rename("Annual_budget"=q10_budget_year_2022) %>% 
  mutate(Year=2022)

q10_2023<-base %>% 
  filter(!is.na(q10_budget_year_2023)) %>% 
  group_by(q10_budget_year_2023) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  rename("Annual_budget"=q10_budget_year_2023) %>% 
  mutate(Year=2023)


# Unir los dataframes
q10_total <- bind_rows(q10_2021, q10_2022, q10_2023)

#q10_total
q10_total<-q10_total %>% arrange(Annual_budget)
# Crear un nuevo data frame con los resultados
q10_total <- q10_total %>%
  pivot_wider(names_from = Year, values_from = c(n, Percentage)) %>% 
  select(1,5:7)


knitr::kable(q10_total) %>% 
  kable_minimal() #imprime cuadro
```


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**BUDGET GROUPED PROPOSAL** 

```{r}

consulta<- base %>%
   group_by(q10_budget_year_2021) %>% 
  summarise(n=n())

consulta
  
# base<- base %>%
#   mutate(q10_budget_grp_2021=case_when
#          (
#            (q10_budget_year_2021=="(h) 250001 - 500000"  |
#            q10_budget_year_2021=="(i) 500001 - 1000000" | 
#            q10_budget_year_2021=="(j) 1000001 - 2000000" |
#            q10_budget_year_2021=="(k) 2000001 - 4000000" |
#            q10_budget_year_2021=="(l) > 4000001") ~ "(h) > 250001",
#            TRUE ~ q10_budget_year_2021))  
# 
# base<- base %>%
#   mutate(q10_budget_grp_2022=case_when
#          (
#            (q10_budget_year_2022=="(h) 250001 - 500000"  |
#            q10_budget_year_2022=="(i) 500001 - 1000000" | 
#            q10_budget_year_2022=="(j) 1000001 - 2000000" |
#            q10_budget_year_2022=="(k) 2000001 - 4000000" |
#            q10_budget_year_2022=="(l) > 4000001") ~ "(h) > 250001",
#            TRUE ~ q10_budget_year_2022))  
# 
# base<- base %>%
#   mutate(q10_budget_grp_2023=case_when
#          (
#            (q10_budget_year_2023=="(h) 250001 - 500000"  |
#            q10_budget_year_2023=="(i) 500001 - 1000000" | 
#            q10_budget_year_2023=="(j) 1000001 - 2000000" |
#            q10_budget_year_2023=="(k) 2000001 - 4000000" |
#            q10_budget_year_2023=="(l) > 4000001") ~ "(h) > 250001",
#            TRUE ~ q10_budget_year_2023))  

q10_2021<-base %>% 
  filter(q9_year_formation<2022) %>% 
  group_by(q10_budget_grp_2021) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  rename("Annual_budget"=q10_budget_grp_2021) %>% 
  mutate(Year=2021)

q10_2022<-base %>% 
  filter(q9_year_formation<2023) %>% 
  group_by(q10_budget_grp_2022) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  rename("Annual_budget"=q10_budget_grp_2022) %>% 
  mutate(Year=2022)

q10_2023<-base %>% 
  filter(!is.na(q10_budget_year_2023)) %>% 
  group_by(q10_budget_grp_2023) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  rename("Annual_budget"=q10_budget_grp_2023) %>% 
  mutate(Year=2023)

# Unir los dataframes
q10_grouped <- bind_rows(q10_2021, q10_2022, q10_2023)

#q10_total
q10_grouped<-q10_grouped %>% arrange(Annual_budget)
# Crear un nuevo data frame con los resultados
q10_grouped <- q10_grouped %>%
  pivot_wider(names_from = Year, values_from = c(n, Percentage)) %>% 
  select(1,5:7)


q10_grouped

```



**--Lecture -----------------------------------------------------------------------**

This grouping maintains interesting proportions respecting the way the question was asked. Only the highest amounts are grouped together.

We suggest using the year 2023 as a crossover variable for other questions as it accounts for size.

**------------------------------------------------------------------------------------------------**



**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

Q11. In 2020 (during COVID-19 pandemic), how was your budget affected?



```{r registered, echo=F, message=F, warning=F}

q11<-base %>%
  filter(!is.na(q11_covid_incidence) & q11_covid_incidence!="not_applicable" & q11_covid_incidence!="")%>%
  group_by(q11_covid_incidence) %>% 
   mutate(q11_covid_incidence= case_when(
    q11_covid_incidence=="grown_substantially" ~ "1 Grow substantively",
    q11_covid_incidence=="grown_slightly" ~ "2 Grow slightly",
    q11_covid_incidence=="stayed_the_same" ~ "3 Stay the same",
    q11_covid_incidence=="decreased_slightly" ~ "4 Decrease slightly",
    q11_covid_incidence=="decreased_substantially" ~ "5 Decrease substantially",
   # q11_covid_incidence=="not_applicable" ~ NA,
    TRUE ~ NA)) %>%  
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  arrange(q11_covid_incidence) 

knitr::kable(q11) %>% 
  kable_minimal()


```




```{r}

ggplot(q11, aes(x = q11_covid_incidence, y = Percentage, fill = q11_covid_incidence)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5, size = 3.5) +
  labs(title = "Covid incidence",
       x = " ",
       y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "none")

```
**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

##CROSSTABS Q10 - only 2023


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**2023 budget BY AWID FOCUS SUBJECTS**

(first option)

```{r}
#q10_budget_grp_2023

 ## Anti-caste 
q10q4_anti_caste<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.anti_caste)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.anti_caste,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q10q4_peace<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.anti_militarization)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.anti_militarization,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q10q4_climate<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.climate_justice)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.climate_justice,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q10q4_anti_rights<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.countering_anti_gender)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.countering_anti_gender,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q10q4_care<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.holistic_safety_protection_collective_care)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q10q4_lesbian<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.lesbian_bisexual_queer_rights)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q10q4_sex_workers<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.sex_workers_rights)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.sex_workers_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q10q4_trans<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_forms_organizing.trans_non_binary_rights)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.trans_non_binary_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q10q4_others<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q10_budget_grp_2023,q4_awid_focus_no)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_awid_focus_no,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )

q10q4_all<-bind_rows(q10q4_anti_caste,q10q4_peace,q10q4_climate,q10q4_anti_rights,q10q4_care,q10q4_lesbian,q10q4_sex_workers,q10q4_trans,q10q4_others)


q10q4_all <-q10q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q10_budget_grp_2023,percentage) %>%  arrange(q10_budget_grp_2023)

#q5q4_all
qry_w<-q10q4_all %>% pivot_wider(names_from = q10_budget_grp_2023, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```


**--Lecture-----------------------------------------------------------------------**

Here we can analyze for the organizations according to their budget, in which issues they work or are more represented.

For example, among the organizations with Zero budget there is a higher proportion of those working on Sex workers rights issues than among the organizations with more funding.

**------------------------------------------------------------------------------------------------**


**AWID FOCUS SUBJECTS BY 2023 budget**

This is the reverse crossover: we see how the amount of the budget is distributed within each of the groups. Remember that the topics overlap.


```{r}
#q10_budget_grp_2023

##delte variables to clean environment
rm(list=setdiff(ls(), "base"))

 ## Anti-caste 
q10q4_anti_caste<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.anti_caste,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.anti_caste,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q10q4_peace<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.anti_militarization,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.anti_militarization,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q10q4_climate<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.climate_justice,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.climate_justice,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q10q4_anti_rights<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.countering_anti_gender,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.countering_anti_gender,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q10q4_care<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.holistic_safety_protection_collective_care,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q10q4_lesbian<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.lesbian_bisexual_queer_rights,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q10q4_sex_workers<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.sex_workers_rights,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.sex_workers_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q10q4_trans<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_forms_organizing.trans_non_binary_rights,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_forms_organizing.trans_non_binary_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q10q4_others<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="98" & q10_budget_grp_2023!="") %>%
  group_by(q4_awid_focus_no,q10_budget_grp_2023)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q10_budget_grp_2023,q4_grouped=q4_awid_focus_no,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )

q10q4_all<-bind_rows(q10q4_anti_caste,q10q4_peace,q10q4_climate,q10q4_anti_rights,q10q4_care,q10q4_lesbian,q10q4_sex_workers,q10q4_trans,q10q4_others)


q10q4_all <-q10q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q10_budget_grp_2023,percentage) %>%  arrange(q10_budget_grp_2023)

#q5q4_all
qry_w<-q10q4_all %>% pivot_wider(names_from = q10_budget_grp_2023, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```



**--Lecture-----------------------------------------------------------------------**


In this case, the distribution is reversed. For each of the work topics, we can see how the Budget is for the organizations that work on these topics.

**------------------------------------------------------------------------------------------------**






**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**2023 budget by registration**



```{r}

##borrar las variables para evitar problemas
#rm(list=setdiff(ls(), "base"))

#q6_geo_scope

q6q5<-base %>%
  filter(!is.na(q10_budget_grp_2023) & q10_budget_grp_2023!="" & !is.na(q5_registered) & q5_registered!="") %>%
  group_by(q10_budget_grp_2023,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(=recode(q6_geo_scope,
          "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Diaspora",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"
         ) ) %>%
  select(q5_registered,Scope=q6_geo_scope,percentage)

#q6q5
qry_w<-q6q5 %>% pivot_wider(names_from = Scope, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))

knitr::kable(qry_w) %>% 
  kable_minimal()


```

```{r}
#q5q2

qry_graph<-q6q5 %>% filter((q5_registered=="y_registered" | q5_registered=="n_registered") )
                      #& (Scope=="Nationally"  | Scope=="Locally" | Scope=="Regionally"))
#qry_graph

ggplot(qry_graph, aes(x = Scope, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Registration by Geographic scope (%)") +                
  theme_light()+
 geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) +
   coord_flip()

```












