---
title: "WITM"
date: "`r Sys.Date()`"
output: html_document
---

#WITM Analysis - section 1 - v2

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)
library(xlsx)

rm(list = ls())

```

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

This report filters only people who answered Q0=yes (i.e. who agree to answer the survey) and does not filter on question q1.

```{r upload, echo=T, message=F, warning=F}

# OPEN CSV file
witm <- read.csv("Data/WITM_cleaned_09232024.csv")

source(file="WITM_variables_include.R") 

base<-witm
```
___



___
##CROSSTABS 


**AWID FOCUS SUBJECTS BY REGISTRATION**


A crosstabulation (bivariate) of the combination of registration and subject of the organisation 


```{r}

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n


q4_1 <- base %>%
  group_by(q5_registered) %>% 
  summarise(Total = n(),
            LGTBIQ= sum(q4_awid_LGBTIQ==1),
            Young= sum(q4_awid_young==1),
            Sex_workers=sum(q4_awid_sex==1),
            Anti_caste=sum(q4_awid_anticaste==1),
            Climate=sum(q4_awid_climate==1),
            Countering_anti=sum(q4_awid_antigender==1),
            Harm_reduction=sum(q4_awid_harm==1),
            Disability_rights=sum(q4_awid_disability==1)) 


write.xlsx2(as.data.frame(q4_1), "cuadros\\section_1.xlsx", row.names = FALSE, sheetName ="q4_1",append = TRUE)    

q4_1


```





**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**


**SUBJECTS GROUPED BY SCOPE**


```{r}

q4_2 <- base %>%
  group_by(q6_geo_scope) %>% 
  summarise(Total = n(),
            LGTBIQ= sum(q4_awid_LGBTIQ==1),
            Young= sum(q4_awid_young==1),
            Sex_workers=sum(q4_awid_sex==1),
            Anti_caste=sum(q4_awid_anticaste==1),
            Climate=sum(q4_awid_climate==1),
            Countering_anti=sum(q4_awid_antigender==1),
            Harm_reduction=sum(q4_awid_harm==1),
            Disability_rights=sum(q4_awid_disability==1)) 


write.xlsx2(as.data.frame(q4_2), "cuadros\\section_1.xlsx", row.names = FALSE, sheetName ="q4 scope",append = TRUE)    

q4_2


```

**SUBJECTS GROUPED BY YEAR OF FORMATION**



```{r}

q4_3 <- base %>%
  group_by(q9_year_formation_agrup) %>% 
  summarise(Total = n(),
            LGTBIQ= sum(q4_awid_LGBTIQ==1),
            Young= sum(q4_awid_young==1),
            Sex_workers=sum(q4_awid_sex==1),
            Anti_caste=sum(q4_awid_anticaste==1),
            Climate=sum(q4_awid_climate==1),
            Countering_anti=sum(q4_awid_antigender==1),
            Harm_reduction=sum(q4_awid_harm==1),
            Disability_rights=sum(q4_awid_disability==1)) 


write.xlsx2(as.data.frame(q4_3), "cuadros\\section_1.xlsx", row.names = FALSE, sheetName ="q4 year",append = TRUE)    

q4_3


```

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope by registration**


A crosstabulation (bivariate) of the combination of registered and scope

```{r}

##borrar las variables para evitar problemas
#rm(list=setdiff(ls(), "base"))

q6q5<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="" & !is.na(q5_registered) & q5_registered!="") %>%
  group_by(q6_geo_scope,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q6_geo_scope=recode(q6_geo_scope,
          "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Diaspora",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"
         ) ) %>%
  select(q5_registered,Scope=q6_geo_scope,percentage)

#q6q5
qry_w<-q6q5 %>% pivot_wider(names_from = Scope, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))
qry_w

write.xlsx2(as.data.frame(qry_w), "cuadros\\section_1.xlsx", row.names = FALSE, sheetName ="scop_by_reg",append = TRUE)    


knitr::kable(qry_w) %>% 
  kable_minimal()


```


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Region by register**

This is made now only for Locally and National organisations

```{r region_q5, echo=F, message=F, warning=F}


# 
reg_1 <- base %>%
  group_by(q5_registered) %>% 
  summarise(Total= n(),
            "1. Latin America & the Caribbean"=sum(region_1==1),
            "2. Western Europe & North America"=sum(region_2==1),
            "3. Eastern, Southeast and Central Europe"=sum(region_3==1),
            "4. Africa"= sum(region_4==1),
            "5. Asia & the Pacific"=sum(region_5==1),
            "6. Central Asia & Caucasus"=sum(region_6==1),
            "7. South West Asia/Middle East & North Africa"=sum(region_7==1))

reg_1
write.xlsx2(as.data.frame(reg_1), "cuadros\\section_2.xlsx", row.names = FALSE, sheetName ="region_by_reg",append = TRUE)    


knitr::kable(t(reg_1)) %>% 
  kable_minimal()

```

```{r region_q5, echo=F, message=F, warning=F}


# 
reg_2 <- base %>%
  group_by(q6_geo_scope) %>% 
  summarise(Total= n(),
            "1. Latin America & the Caribbean"=sum(region_1==1),
            "2. Western Europe & North America"=sum(region_2==1),
            "3. Eastern, Southeast and Central Europe"=sum(region_3==1),
            "4. Africa"= sum(region_4==1),
            "5. Asia & the Pacific"=sum(region_5==1),
            "6. Central Asia & Caucasus"=sum(region_6==1),
            "7. South West Asia/Middle East & North Africa"=sum(region_7==1))

reg_2
write.xlsx2(as.data.frame(reg_2), "cuadros\\section_2.xlsx", row.names = FALSE, sheetName ="region_by_scope",append = TRUE)    


knitr::kable(t(reg_2)) %>% 
  kable_minimal()

```





```{r region_q5, echo=F, message=F, warning=F}


# 
reg_2 <- base %>%
  group_by(q9_year_formation_agrup) %>% 
  summarise(Total= n(),
            "1. Latin America & the Caribbean"=sum(region_1==1),
            "2. Western Europe & North America"=sum(region_2==1),
            "3. Eastern, Southeast and Central Europe"=sum(region_3==1),
            "4. Africa"= sum(region_4==1),
            "5. Asia & the Pacific"=sum(region_5==1),
            "6. Central Asia & Caucasus"=sum(region_6==1),
            "7. South West Asia/Middle East & North Africa"=sum(region_7==1))

reg_2
write.xlsx2(as.data.frame(reg_2), "cuadros\\section_2.xlsx", row.names = FALSE, sheetName ="region_by_year",append = TRUE)    


knitr::kable(t(reg_2)) %>% 
  kable_minimal()

```
___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year of formation & Register**


```{r year_register, echo=F, message=F, warning=F}



q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup) & !is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>% 
  group_by(q9_year_formation_agrup,q5_registered) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  select(q9_year_formation_agrup,q5_registered,percentage)


qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))

write.xlsx2(as.data.frame(qry_w), "cuadros\\section_2.xlsx", row.names = FALSE, sheetName ="year_by_reg",append = TRUE)    


knitr::kable(qry_w) %>% 
  kable_minimal()



```


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year by Gegraphically Scope**



```{r year_q6, echo=F, message=F, warning=F}

#rm(list=setdiff(ls(), "base"))

qry<-base %>%
    group_by(q6_geo_scope) %>%
  summarise(n=n())

qry

q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup) & !is.na(q6_geo_scope)) %>% 
  group_by(q6_geo_scope,q9_year_formation_agrup) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  mutate(q6_geo_scope=recode(q6_geo_scope,
     "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
         "transnationally_focused"="Transnationally",
         "globally_focused"="Global")) %>%
  select(q9_year_formation_agrup,q6_geo_scope,percentage)


q8

qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage)
       
 
write.xlsx2(as.data.frame(qry_w), "cuadros\\section_2.xlsx", row.names = FALSE, sheetName ="year_by_scope",append = TRUE)    


knitr::kable(qry_w) %>% 
  kable_minimal()



```






