---
title: "Where is the Money for Feminist Organizing? Survey for feminist, women’s rights and gender justice movements, groups and organizations"
date: "`r Sys.Date()`"
output: html_document
---

#WITM follow up

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

rm(list = ls())

```


**Database upload**

```{r upload, echo=T, message=F, warning=F}


# To upload CSV file
#datos <- read.csv2("Data/WITM_csv_last.csv")
datos <- read.csv("Data/WITM_final_cleaned_08_sept.csv")

# To upload xlsx file
#datos<- read_xlsx("WITM_xls_value2.xlsx", sheet = 1)
```


___

**Answers**

Number oi answers by date


```{r}

#2024-05-23 08:37:41.178000-04:00
datos$date <-  as.Date(datos$end,'%Y-%m-%d')



answers_by_date<-datos  %>% 
  group_by(date) %>%  
  summarise(qt=n())


ggplot(answers_by_date, aes(x = date, y=qt)) +                      
  geom_bar(stat="identity",width=0.5, colour="red", fill="skyblue") +
  labs(x="date",y= "Number") +                 
  ggtitle("Number of answers by date") +                
  theme_bw(base_size = 12)+  
  geom_text(aes(label = signif(qt)), nudge_y = 3)
```


___

**Consent:**

Q1. I consent to take the WITM survey on behalf of my group, organization or movement.

```{r consent, echo=F, message=F, warning=F}

q0<-datos %>%
  group_by(q0_consent) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  rename("Consent"=q0_consent)

knitr::kable(q0) %>% 
  kable_minimal()


#From now on, only those who have given their consent to respond to the survey will be considered for analysis

base<-datos %>% 
  filter(q0_consent=="yes")
```
___

**Group information:**

Q2. Which of the following statements best describes your group, organization and/or movement?

```{r info, echo=F, message=F, warning=F}
q1<-base %>%
  group_by(q1_description) %>% 
  mutate(q1_description=forcats::fct_recode(as_factor(q1_description),
                                                     "We promote the rights of women or girls or trans or gender diverse people in all their intersecting identities and this is the 'primary focus of all our work'" = "primary_focus",
                                            "We promote the rights of women or girls or trans or gender diverse people with intersecting identities 'through specific project(s)', but not as the primary focus of our work" = "specific_projects",
                                            "Other" = "98")) %>%
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q1_description)) %>% 
  rename("Description"=q1_description)


knitr::kable(q1) %>% 
  kable_minimal()
```


```{r info_other, echo=F, message=F, warning=F}
#Other responses

q1_otro<-base %>%
  filter(q1_description==98) %>% 
  group_by(q1_description_group) %>% 
  summarise(n=n()) %>% 
  select("Other"=q1_description_group)

knitr::kable(q1_otro) %>% 
  kable_minimal()

```
___

**Organization names:**

Q3. The name of your group, organization and/or movement

```{r name, echo=F, message=F, warning=F}
q2<-base %>%
  filter(!is.na(q2_name)) %>% 
  group_by(q2_name) %>% 
  summarise(n=n()) %>% 
  select("Organization names"=q2_name) %>% 
  slice(-1)

#knitr::kable(q2) %>% 
#  kable_minimal()

```
___

**Type of organization**

Q4. Which of the following forms of organizing best describes your group, organization and/or movement?

*This is a multiple-choice question so the sum of the % does NOT add up to 100.*

```{r type, echo=F, message=F, warning=F}

#Total valid responses for calculating percentage

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(starts_with("q4_forms_organizing."))

#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Black rights/ Black feminist rights"="q4_forms_organizing.black_rights",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Crisis response"="q4_forms_organizing.crisis_response",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                "Digital rights"="q4_forms_organizing.digital_rights",
                                "Disability rights and justice"="q4_forms_organizing.disability_rights",
                                "Displaced, migrant and refugee rights"="q4_forms_organizing.displaced_migrant_refugee_rights",
                                "Economic justice, rights and alternatives"="q4_forms_organizing.economic_justice",
                                "Freedom of information and media"="q4_forms_organizing.information_media_freedom",
                                "Harm reduction"="q4_forms_organizing.harm_reduction",
                                "Ending gender based violence"="q4_forms_organizing.end_gender_violence",
                                "Pleasure and bodily care"="q4_forms_organizing.pleasure_bodily_care",
                                "Resisting the war on drugs"="q4_forms_organizing.resisting_war_on_drugs",
                                "Rights for people living with HIV+"="q4_forms_organizing.rights_for_people_living_with_hiv",
                                "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Human rights"="q4_forms_organizing.human_rights",
                                "Indigenous rights"="q4_forms_organizing.indigenous_rights",
                                "Intersex rights"="q4_forms_organizing.intersex_rights",
                                "Labour rights"="q4_forms_organizing.labour_rights",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Racial justice"="q4_forms_organizing.racial_justice",
                                "Religious and ethnic minority rights"="q4_forms_organizing.religious_ethnic_minority_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Sexual and reproductive health & rights (SRHR) and bodily autonomy"="q4_forms_organizing.srhr_bodily_autonomy",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Women's rights"="q4_forms_organizing.womens_rights",
                                "Young feminists"="q4_forms_organizing.young_feminists",
                                "Girls’ movements"="q4_forms_organizing.girls_movements",
                                "Human rights defenders at risk"="q4_forms_organizing.hr_defenders_at_risk",
                                "Other"="q4_forms_organizing.98"))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization type"=q4)


knitr::kable(q4) %>% 
  kable_minimal()

```

___


**Register**

Q5. Is your group, organization and/or movement registered?

```{r registered, echo=F, message=F, warning=F}

q5<-base %>%
  group_by(q5_registered) %>% 
  mutate(q5_registered= case_when(
    q5_registered=="y_registered" ~ "Yes",
    q5_registered=="n_registered" ~ "No",
    q5_registered==98 ~ "Other",
    TRUE ~ NA)) %>%  
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q5_registered)) %>% 
  rename("Register"=q5_registered)


knitr::kable(q5) %>% 
  kable_minimal()

```
___

**Scope:**

Q6. What is the geographical scope of your work?

```{r scope, echo=F, message=F, warning=F}

q6<-base %>% 
  group_by(q6_geo_scope) %>% 
  mutate(q6_geo_scope=forcats::fct_recode(as_factor(q6_geo_scope),
                                                     "Locally" = "locally_focused",
                                            "Nationally" = "nationally_focused",
                                          "Work from diaspora, refuge and/or exile" = "diaspora_and_or_exile",
                                          "Regionally" = "regionally_focused",
                                          "Transnationally" = "transnationally_focused",
                                          "Global" = "globally_focused")) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(q6_geo_scope) %>% 
  rename("Geo scope"=q6_geo_scope)


knitr::kable(q6) %>% 
  kable_minimal()
```
___

**Region:**

Q7. Indicate in which region(s) your group, organization and/or movement works

*Reading: 22% of the organizations work in South Asia.
Organizations working locally, regionally or globally were consolidated.*


```{r region, echo=F, message=F, warning=F}

q7_a<-base %>% 
  filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one) %>%
    mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%   summarise(n=n())%>% 
  rename(q7=q7_region_one) %>% 
  arrange(q7)

q7_select<-base %>% 
  select(starts_with("q7_region_multiple.")) %>% 
  filter(!is.na(q7_region_multiple.samerica))


q7_b<-q7_select%>% 
  summarize_all(sum) %>% 
  gather(q7, n) %>% 
  mutate(q7= str_replace(q7, "q7_region_multiple.", "")) %>% 
  mutate(q7=forcats::fct_recode(as_factor(q7),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica"))


q7_final <- q7_a %>% left_join(q7_b, by = "q7") %>% 
  mutate(n=n.x+n.y) %>% 
  select(-n.x,-n.y, "Region"=q7) %>%
  mutate(porcentaje=round((n/total)*100,1)) %>% 
  arrange(desc(porcentaje)) 
  


knitr::kable(q7_final) %>% 
  kable_minimal()

```
___

**Country:**

Q8. Which countries are you working in?


```{r q6, recho=F, message=F, warning=F}

#Convertir campos vacíos de la variable country en NA
 base <- base %>%
  mutate(q8_country = na_if(q8_country, ""))

base<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%
  mutate(q8_country=forcats::fct_recode(as_factor(q8_country),
                                      "Afghanistan"="afghanistan",
                                      "Albania"="albania",
                                      "Algeria"="algeria",
                                      "American Samoa"="american_samoa",
                                      "Andorra"="andorra",
                                      "Angola"="angola",
                                      "Anguilla"="anguilla",
                                      "Antigua and Barbuda"="antigua_and_barbuda",
                                      "Argentina"="argentina",
                                      "Armenia"="armenia",
                                      "Aruba"="aruba",
                                      "Australia"="australia",
                                      "Austria"="austria",
                                      "Azerbaijan"="azerbaijan",
                                      "Bahamas"="bahamas",
                                      "Bahrain"="bahrain",
                                      "Bangladesh"="bangladesh",
                                      "Barbados"="barbados",
                                      "Belarus"="belarus",
                                      "Belgium"="belgium",
                                      "Belize"="belize",
                                      "Benin"="benin",
                                      "Bhutan"="bhutan",
                                      "Bolivia"="bolivia",
                                      "Bonaire, Sint Eustatius and Saba"="bonaire_sint_eustatius_saba",
                                      "Bosnia and Herzegovina"="bosnia_and_herzegovina",
                                      "Botswana"="botswana",
                                      "Brazil"="brazil",
                                      "British Virgin Islands"="british_virgin_islands",
                                      "Brunei Darussalam"="brunei_darussalam",
                                      "Bulgaria"="bulgaria",
                                      "Burkina Faso"="burkina_faso",
                                      "Burundi"="burundi",
                                      "Cabo Verde"="cabo_verde",
                                      "Cambodia"="cambodia",
                                      "Cameroon"="cameroon",
                                      "Canada"="canada",
                                      "Cayman Islands"="cayman_islands",
                                      "Central African Republic"="cafrican_republic",
                                      "Chad"="chad",
                                      "Chile"="chile",
                                      "China"="china",
                                      "Colombia"="colombia",
                                      "Comoros"="comoros",
                                      "Congo"="congo",
                                      "Cook Islands"="cook_islands",
                                      "Costa Rica"="costa_rica",
                                      "Côte d'Ivoire"="côte_divoire",
                                      "Croatia"="croatia",
                                      "Cuba"="cuba",
                                      "Curaçao"="curaçao",
                                      "Cyprus"="cyprus",
                                      "Czech Republic"="czech_republic",
                                      "Dem. People's Republic of Korea"="dem_peoples_rep_of_korea",
                                      "Democratic Republic of the Congo"="democratic_republic_of_the_congo",
                                      "Denmark"="denmark",
                                      "Djibouti"="djibouti",
                                      "Dominica"="dominica",
                                      "Dominican Republic"="dominican_republic",
                                      "Ecuador"="ecuador",
                                      "Egypt"="egypt",
                                      "El Salvador"="el_salvador",
                                      "Equatorial Guinea"="equatorial_guinea",
                                      "Eritrea"="eritrea",
                                      "Estonia"="estonia",
                                      "Eswatini"="eswatini",
                                      "Ethiopia"="ethiopia",
                                      "Fiji"="fiji",
                                      "Finland"="finland",
                                      "France"="france",
                                      "French Guiana"="french_guiana",
                                      "French Polynesia"="french_polynesia",
                                      "Gabon"="gabon",
                                      "Gambia"="gambia",
                                      "Georgia"="georgia",
                                      "Germany"="germany",
                                      "Ghana"="ghana",
                                      "Greece"="greece",
                                      "Greenland"="greenland",
                                      "Grenada"="grenada",
                                      "Guadeloupe"="guadeloupe",
                                      "Guam"="guam",
                                      "Guatemala"="guatemala",
                                      "Guinea"="guinea",
                                  "Guinea-Bissau"="guinea_bissau",
                                      "Guyana"="guyana",
                                      "Haiti"="haiti",
                                      "Honduras"="honduras",
                                      "Hong Kong"="hong_kong",
                                      "Hungary"="hungary",
                                      "Iceland"="iceland",
                                      "India"="india",
                                      "Indonesia"="indonesia",
                                      "Iran"="iran",
                                      "Iraq"="iraq",
                                      "Ireland"="ireland",
                                      "Israel"="israel",
                                      "Italy"="italy",
                                      "Jamaica"="jamaica",
                                      "Japan"="japan",
                                      "Jordan"="jordan",  
                                      "Kazakhstan"="kazakhstan",
                                  "Kenya"="kenya",
                                  "Kiribati"="kiribati",
                                  "Kuwait"="kuwait",
                                  "Kyrgyzstan"="kyrgyzstan",
                                  "Lao People's Democratic Republic"="lao_peoples_democratic_republic",
                                  "Latvia"="latvia",
                                  "Lebanon"="lebanon",
                                  "Lesotho"="lesotho",
                                  "Liberia"="liberia",
                                  "Libya"="libya",
                                  "Liechtenstein"="liechtenstein",
                                  "Lithuania"="lithuania",
                                  "Luxembourg"="luxembourg",
                                  "Macao"="macao",
                                  "Madagascar"="madagascar",
                                  "Malawi"="malawi",
                                  "Malaysia"="malaysia",
                                  "Maldives"="maldives",
                                  "Mali"="mali",
                                  "Malta"="malta",
                                  "Marshall
                                  Islands"="marshall_islands",
                                  "Martinique"="martinique",
                                  "Mauritania"="mauritania",
                                  "Mauritius"="mauritius",
                                  "Mayotte"="mayotte",
                                  "Mexico"="mexico",
                                  "Micronesia (Fed. States of)"="micronesia_fed_states_of",
                                  "Monaco"="monaco",
                                  "Mongolia"="mongolia",
                                  "Montenegro"="montenegro",
                                  "Montserrat"="montserrat",
                                  "Morocco"="morocco",
                                  "Mozambique"="mozambique",
                                  "Myanmar"="myanmar",
                                  "Namibia"="namibia",
                                  "Nauru"="nauru",
                                  "Nepal"="nepal",
                                  "Netherlands"="netherlands",
                                  "New Caledonia"="new_caledonia",
                                  "New Zealand"="new_zealand",
                                  "Nicaragua"="nicaragua",
                                  "Niger"="niger",
                                  "Nigeria"="nigeria",
                                "Niue"="niue",
                                "North Macedonia"="north_macedonia",
                                "Northern Mariana Islands"="northern_mariana_islands",
                                "Norway"="norway",
                                "Oman"="oman",
                                "Pakistan"="pakistan",
                                "Palau"="palau",
                                "Palestine"="palestine",
                                "Panama"="panama",
                                "Papua New Guinea"="papua_new_guinea",
                                "Paraguay"="paraguay",
                                "Peru"="peru",
                                "Philippines"="philippines",
                                "Poland"="poland",
                                "Portugal"="portugal",
                                "Puerto Rico"="puerto_rico",
                                "Qatar"="qatar",
                                "Republic of Korea"="republic_of_korea",
                                "Republic of Moldova"="republic_of_moldova",
                                "Réunion"="reunion",
                                "Romania"="romania",
                                "Russia"="russia",
                                "Rwanda"="rwanda",
                                "Saint Barthélemy"="saint_barthelemy",
                                "Saint Helena"="saint_helena",
                                "Saint Kitts and Nevis"="saint_kitts_and_nevis",
                                "Saint Lucia"="saint_lucia",
                                "Saint Martin (French part)"="saint_martin_french_part",
                                "Saint Vincent and the Grenadines"="saint_vincent_and_the_grenadines",
                                "Samoa"="samoa",
                                "San Marino"="san_marino",
                                "Sao Tome and Principe"="sao_tome_and_principe",
                                "Saudi Arabia"="saudi_arabia",
                                "Senegal"="senegal",
                                "Serbia"="serbia",
                                "Seychelles"="seychelles",
                                "Sierra Leone"="sierra_leone",
                                "Singapore"="singapore",
                                "Sint Maarten (Dutch part)"="sint_maarten_dutch_part",
                                "Slovakia"="slovakia",
                                "Slovenia"="slovenia",
                                "Solomon Islands"="solomon_islands",
                                "Somalia"="somalia",
                                "South Africa"="south_africa",
                                "South Sudan"="south_sudan",
                                "Spain"="spain",
                                "Sri Lanka"="sri_lanka",
                                "Sudan"="sudan",
                                "Suriname"="suriname",
                                "Sweden"="sweden",
                                "Switzerland"="switzerland",
                                "Syrian Arab Republic"="syrian_arab_republic",
                                "Taiwan"="taiwan",
                                "Tajikistan"="tajikistan",
                                "Tanzania"="tanzania",
                                "Thailand"="thailand",
                                "Timor-Leste"="timor_leste",
                                "Togo"="togo",
                                "Tokelau"="tokelau",
                                "Tonga"="tonga",
                                "Trinidad and Tobago"="trinidad_and_tobago",
                                "Tunisia"="tunisia",
                                "Turkey"="turkey",
                                "Turkmenistan"="turkmenistan",
                                "Turks and Caicos Islands"="turks_and_caicos_islands",
                                "Tuvalu"="tuvalu",
                                "Uganda"="uganda",
                                "Ukraine"="ukraine",
                                "United Arab Emirates"="united_arab_emirates",
                                "United Kingdom"="united_kingdom",
                                "United States of America"="united_states_of_america",
                                "Uruguay"="uruguay",
                                "Uzbekistan"="uzbekistan",
                                "Vanuatu"="vanuatu",
                                "Venezuela (Bolivarian Republic of)"="venezuela_bolivarian_republic_of",
                                "Viet Nam"="viet_nam",
                                "Wallis and Futuna Islands"="wallis_and_futuna_islands",
                                "Western Sahara"="western_sahara",
                                "Yemen"="yemen",
                                "Zambia"="zambia",
                                "Zimbabwe"="zimbabwe",
                                "Other South America"="country_other1",
                                "Other Central America & Mexico"="country_other2",
                                "Other North America"="country_other3",
                                "Other Caribbean"="country_other4",
                                "Other South Asia"="country_other5",
                                "Other Southeast Asia"="country_other6",
                                "Other East Asia"="country_other7",
                                "Other The Pacific"="country_other8",
                                "Other South West Asia/Middle East"="country_other9",
                                "Other Central Asia & Caucasus"="country_other10",
                                "Other Eastern Europe, Southeast Europe and Central Europe"="country_other11",
                                "Other Western Europe"="country_other13",

                              "Other West Africa"="country_other14",
                              "Other East Africa"="country_other15",
                              "Other Southern Africa"="country_other16",
                              "Other Central Africa"="country_other17",
                              "Other North Africa"="country_other18"))


q8<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one, q8_country) %>% 
  summarise(n=n()) 
#%>% mutate(Percentage=round((n/sum(n))*100,1))

knitr::kable(q8) %>% 
  kable_minimal()

```
___

**Year of formation:**

Q9. What year was your group, organization and/ or movement formed?

*Reading: 36% of the respondent organizations were formed between the years 2015 and 2020, while around 13% were formed from the year 2021 onwards*
```{r year, echo=F, message=F, warning=F}
q9<-base %>% 
  mutate(q9_year_formation_agrup=case_when(
    q9_year_formation==2023 ~  1,
    q9_year_formation==2022 ~  2,
    q9_year_formation==2021 ~  3,
    q9_year_formation<2021 & q9_year_formation>2014 ~  4,
    q9_year_formation<2015 & q9_year_formation>2009 ~  5,
    q9_year_formation<2010 & q9_year_formation>1999 ~  6,
    is.na(q9_year_formation) ~ NA,
    TRUE ~  7)) %>%
  mutate(q9_year_formation_agrup=forcats::fct_recode(as_factor(q9_year_formation_agrup),
                                                     "Año 2023" = "1",
                                                     "Año 2022" = "2",
                                                     "Año 2021" = "3",
                                                     "Entre 2015 y 2020" = "4",
                                                     "Entre 2010 y 2014" = "5",
                                                     "Entre 2000 y 2009" = "6",
                                                     "Antes del 2000" = "7")) %>% 
  filter(!is.na(q9_year_formation_agrup)) %>% 
  group_by(q9_year_formation_agrup) %>% 
  summarise(total=n()) %>% 
  mutate(porcentaje=round((total/sum(total))*100,1)) %>% 
  arrange(q9_year_formation_agrup) %>% 
  rename("Year formation"=q9_year_formation_agrup)


knitr::kable(q9) %>% 
  kable_minimal()
```
___

**External founding:**

Q13. Between 2021 and 2023, has your group, organization and/or movement received any external funding?


```{r ef, echo=F, message=F, warning=F}
q13<-base %>%
  group_by(q13_ext_funding) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  rename("External funding"=q13_ext_funding)
 

knitr::kable(q13) %>% 
  kable_minimal()
```
___

**Language:**

Q46. In which language did you answer the survey?

```{r language, echo=F, message=F, warning=F}

q46<-base %>% 
  mutate(q46_language=case_when(
    q46_language=="english" ~ "English",
    q46_language=="spanish" ~ "Spanish",
    q46_language=="french" ~ "French",
    q46_language=="portuguese" ~ "Portuguese",
    q46_language=="arabic" ~ "Arabic",
    q46_language=="russian" ~ "Russian",
    TRUE ~ NA)) %>% 
  group_by(q46_language) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(q46_language) %>% 
  rename("Language"=q46_language)


knitr::kable(q46) %>% 
  kable_minimal()

```

___

##Previous WITM:

Q45. Did anyone from your group, organization and/or movement respond to AWID’s Where is the Money survey in 2008 or 2011?

```{r previous, echo=F, message=F, warning=F}


q45<-base %>%
  group_by(q45_previous_response) %>% 
  mutate(q45_previous_response=forcats::fct_recode(as_factor(q45_previous_response),
                                                     "Yes" = "yes",
                                            "No" = "no",
                                            "Don't know" = "99")) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q45_previous_response)) %>% 
  rename("Previous response"=q45_previous_response)


knitr::kable(q45) %>% 
  kable_minimal()
```

