---
title: "Where is the Money for Feminist Organizing? Survey for feminist, women’s rights and gender justice movements, groups and organizations"
date: "`r Sys.Date()`"
output: html_document
---

#WITM follow up

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)
library(xlsx)

rm(list = ls())

```


**Database upload**

```{r upload, echo=T, message=F, warning=F}


# To upload CSV file
witm <- read.csv2("Data/WITM_csv_0710.csv")

#2024-05-23 08:37:41.178000-04:00
witm$date <-  as.Date(witm$end,'%Y-%m-%d')


#names(witm)
# To upload xlsx file
#datos<- read_xlsx("WITM_xls_value2.xlsx", sheet = 1)
```

```{r}
#witm$date

witm$date_s <-  paste(format(as.Date(witm$date,format="%Y-%m-%d"), format = "%m"), format(as.Date(witm$date,format="%Y-%m-%d"), format = "%d"), sep ="-", collapse=NULL)

#tmp = cbind("GAD", "AB")
```


___

**Number of answers by date** 

```{r}
answers_by_date<-witm  %>% 
  group_by(date) %>%  
  summarise(qt=n())


ggplot(answers_by_date, aes(x =  as.POSIXct(date), y=qt)) +                      
  geom_bar(stat="identity",width=0.5, colour="red", fill="skyblue") +
  labs(x="date",y= "Number") +                 
  ggtitle("Number of answers by date") +                
  theme_bw(base_size = 12)+  
  scale_x_datetime(breaks=scales::breaks_pretty(8))+
  geom_text(aes(label = signif(qt)), nudge_y = 3)
```

**--Analysis notes-----------------------------------------------------------------------**

In general the polls always have a high peak on the first day, WITM also shows this. Then there is another spike on 27-28 June, probably a strengthening of communication. On the 4th of July it increases again.

**------------------------------------------------------------------------------------------------**


**Consent:**

Q1. I consent to take the WITM survey on behalf of my group, organization or movement.

```{r consent, echo=F, message=F, warning=F}

q0<-witm %>%
  group_by(q0_consent) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  rename("Consent"=q0_consent)

knitr::kable(q0) %>% 
  kable_minimal()

#write.xlsx2(as.data.frame(q0), "Output/section1.xlsx", row.names = FALSE, sheetName ="q1",append = TRUE)


#From now on, only those who have given their consent to respond to the survey will be considered for analysis

base<-witm %>% 
  filter(q0_consent=="yes")
```
___

**Group information:**

Q2. Which of the following statements best describes your group, organization and/or movement?

```{r info, echo=F, message=F, warning=F}
q1<-base %>%
  group_by(q1_description) %>% 
  mutate(q1_description=forcats::fct_recode(as_factor(q1_description),
                                                     "We promote the rights of women or girls or trans or gender diverse people in all their intersecting identities and this is the 'primary focus of all our work'" = "primary_focus",
                                            "We promote the rights of women or girls or trans or gender diverse people with intersecting identities 'through specific project(s)', but not as the primary focus of our work" = "specific_projects",
                                            "Other" = "98")) %>%
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q1_description)) %>% 
  rename("Description"=q1_description)


knitr::kable(q1) %>% 
  kable_minimal()
```


```{r info_other, echo=F, message=F, warning=F}
#Other responses

q1_otro<-base %>%
  filter(q1_description==98) %>% 
  group_by(q1_description_group) %>% 
  summarise(n=n()) %>% 
  select("Other"=q1_description_group)

knitr::kable(q1_otro) %>% 
  kable_minimal()

```
___

**Organization names:**

Q3. The name of your group, organization and/or movement


```{r name1, echo=F, message=F, warning=F}

n_temp<-sum(base$q2_name=="")
print(paste("The number of organisations that did not answer their name is:",n_temp))


```
**--Analysis notes-----------------------------------------------------------------------**

Very interesting that almost all organisations responded with their name despite the fact that the possibility of not responding is informed and underlined.

**------------------------------------------------------------------------------------------------**

```{r name, echo=F, message=F, warning=F}
q2<-base %>%
  filter(!is.na(q2_name)) %>% 
  group_by(q2_name) %>% 
  summarise(n=n()) %>% 
  select("Organization names"=q2_name) %>% 
  slice(-1)

#knitr::kable(q2) %>% 
#  kable_minimal()

```
___

**Type of organization**

Q4. Which of the following forms of organizing best describes your group, organization and/or movement?

*This is a multiple-choice question so the sum of the % does NOT add up to 100.*

```{r type, echo=F, message=F, warning=F}

#Total valid responses for calculating percentage

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(starts_with("q4_forms_organizing."))
#q4_select

#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Black rights/ Black feminist rights"="q4_forms_organizing.black_rights",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Crisis response"="q4_forms_organizing.crisis_response",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                "Digital rights"="q4_forms_organizing.digital_rights",
                                "Disability rights and justice"="q4_forms_organizing.disability_rights",
                                "Displaced, migrant and refugee rights"="q4_forms_organizing.displaced_migrant_refugee_rights",
                                "Economic justice, rights and alternatives"="q4_forms_organizing.economic_justice",
                                "Freedom of information and media"="q4_forms_organizing.information_media_freedom",
                                "Harm reduction"="q4_forms_organizing.harm_reduction",
                                "Ending gender based violence"="q4_forms_organizing.end_gender_violence",
                                "Pleasure and bodily care"="q4_forms_organizing.pleasure_bodily_care",
                                "Resisting the war on drugs"="q4_forms_organizing.resisting_war_on_drugs",
                                "Rights for people living with HIV+"="q4_forms_organizing.rights_for_people_living_with_hiv",
                                "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Human rights"="q4_forms_organizing.human_rights",
                                "Indigenous rights"="q4_forms_organizing.indigenous_rights",
                                "Intersex rights"="q4_forms_organizing.intersex_rights",
                                "Labour rights"="q4_forms_organizing.labour_rights",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Racial justice"="q4_forms_organizing.racial_justice",
                                "Religious and ethnic minority rights"="q4_forms_organizing.religious_ethnic_minority_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Sexual and reproductive health & rights (SRHR) and bodily autonomy"="q4_forms_organizing.srhr_bodily_autonomy",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Women's rights"="q4_forms_organizing.womens_rights",
                                "Young feminists"="q4_forms_organizing.young_feminists",
                                "Girls’ movements"="q4_forms_organizing.girls_movements",
                                "Human rights defenders at risk"="q4_forms_organizing.hr_defenders_at_risk",
                                "Other"="q4_forms_organizing.98"))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization type"=q4)

#write.xlsx2(as.data.frame(q4), "Output/section1.xlsx", row.names = FALSE, sheetName ="q4",append = TRUE)




knitr::kable(q4) %>% 
  kable_minimal()

```
___

**--Analysis notes-----------------------------------------------------------------------**

Most of the organisations selected many options. Almost all of them defined one of the first three options. Only 10% did not select any of them and in general selected others that can be integrated.

**------------------------------------------------------------------------------------------------**


**Type of organization - grouping**


In order to make it easier to analyse, groups can be made, but they are not mutually exclusive, so they are still multiple options.

THIS CAN BE DEFINED DIFFERENTLY. POSSIBLE GROUPINGS SHOULD BE INDICATED


**Feminist specifit subjects**
Girls’ movements. 
Young feminists .
Countering anti-gender and anti-rights 
Lesbian, Bisexual and queer rights 
Sex workers rights 
Trans and non-binary rights
Intersex rights

**General HR subjects**
Human rights defenders at risk
Economic justice, rights and alternatives
Climate and environmental justice
Anti-militarization and peace
Crisis response
Resisting the war on drugs
Anti-caste
Digital rights
Freedom of information and media

**Intersectionality (minority groups)**
Disability rights and justice
Displaced, migrant and refugee rights
Indigenous rights
Racial justice
Black rights/ Black feminist rights
Religious and ethnic minority rights

**Sexual and reproductive health & rights (and others health rights)**
Rights for people living with HIV+
Holistic safety, protection and collective care
Pleasure and bodily care
Sexual and reproductive health & rights (SRHR) and bodily autonomy

```{r type_grouped, echo=F, message=F, warning=F}

base<- base %>%
  mutate(q4_grouped_feminist=case_when
         (
          (q4_forms_organizing.young_feminists==1 |
          q4_forms_organizing.girls_movements==1  |
          q4_forms_organizing.countering_anti_gender ==1  |
          q4_forms_organizing.lesbian_bisexual_queer_rights==1  |
          q4_forms_organizing.sex_workers_rights==1  |
          q4_forms_organizing.trans_non_binary_rights==1  |
          q4_forms_organizing.intersex_rights==1) ~1, TRUE ~0)) %>%  
   mutate(q4_grouped_hr=case_when
         (
          (
            q4_forms_organizing.hr_defenders_at_risk==1 |
            q4_forms_organizing.economic_justice==1 |
            q4_forms_organizing.climate_justice==1 |
            q4_forms_organizing.anti_militarization==1 |
            q4_forms_organizing.crisis_response==1 |
            q4_forms_organizing.resisting_war_on_drugs==1 |
            q4_forms_organizing.anti_caste==1 |
            q4_forms_organizing.digital_rights==1 |
            q4_forms_organizing.information_media_freedom==1) ~1, TRUE ~0)) %>%  
  
   mutate(q4_grouped_minorities=case_when
         (
          (
            q4_forms_organizing.disability_rights==1 |
            q4_forms_organizing.displaced_migrant_refugee_rights==1 |
            q4_forms_organizing.indigenous_rights==1 |
            q4_forms_organizing.racial_justice==1 |
            q4_forms_organizing.black_rights==1 |
            q4_forms_organizing.religious_ethnic_minority_rights==1 ) ~1, TRUE ~0)) %>% 

   mutate(q4_grouped_srhr=case_when
         (
          (
            q4_forms_organizing.rights_for_people_living_with_hiv==1 |
            q4_forms_organizing.holistic_safety_protection_collective_care==1 |
            q4_forms_organizing.pleasure_bodily_care==1 |
            q4_forms_organizing.srhr_bodily_autonomy==1 ) ~1, TRUE ~0)) 

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(starts_with("q4_grouped"))
#q4_select


#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Feminist specifit subjects"="q4_grouped_feminist",
                                "General HR subjects"="q4_grouped_hr",
                                "Intersectionality (minority groups)"="q4_grouped_minorities",
                                "Sexual and reproductive health & rights (and othershealth rights) "="q4_grouped_srhr"
                                ))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization grouped type"=q4)

#write.xlsx2(as.data.frame(q4), "Output/section1.xlsx", row.names = FALSE, sheetName ="q4",append = TRUE)




knitr::kable(q4) %>% 
  kable_minimal()

```
___

**Organisation type & focused**


```{r q2_q4, echo=F, message=F, warning=F}


q2q4<-base %>%
  group_by(q1_description) %>%
  summarise(total=n(),
 #           fem=sum(q4_grouped_feminist==1),
#            hr=sum(q4_grouped_hr==1),
#            min=sum(q4_grouped_minorities==1),
 #           srhr=sum(q4_grouped_srhr==1),
        'Specific feminist subjects'=round(sum(q4_grouped_feminist==1)/total*100,2),
        'General HR Subjects'=round(sum(q4_grouped_hr==1)/total*100,2),
        'Intersectionality (minority groups)'=round(sum(q4_grouped_minorities==1)/total*100,2),
        'Sexual and reproductive health & rights'=round(sum(q4_grouped_srhr==1)/total*100,2))

q2q4<-arrange(q2q4, desc(q1_description))


knitr::kable(q2q4) %>% 
  kable_minimal()


```

**--Analysis notes-----------------------------------------------------------------------**

"70.2% of feminist organisations (primary_focus) are dedicated to one of the priority issues of the feminist agenda".

As this is a multiple choice question, each row is read independently.

It can be seen that the distribution of issues of feminist organisations (primary_focus) is similar to that of organisations that claim to work on gender issues on a project or cross-cutting basis (specific_projects). Although the former work more regularly on the feminist agenda, the latter are more likely to work on the feminist agenda.

**------------------------------------------------------------------------------------------------**

___


**Register**

Q5. Is your group, organization and/or movement registered?

```{r registered, echo=F, message=F, warning=F}

q5<-base %>%
  group_by(q5_registered) %>% 
  mutate(q5_registered= case_when(
    q5_registered=="y_registered" ~ "Yes",
    q5_registered=="n_registered" ~ "No",
    q5_registered==98 ~ "Other",
    TRUE ~ NA)) %>%  
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(n)) %>% 
  rename("Register"=q5_registered)

knitr::kable(q5) %>% 
  kable_minimal()

```

___


**Register by type of organisation**



```{r q5_q2, echo=F, message=F, warning=F}

q5q2<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="" & !is.na(q1_description)) %>%
  group_by(q1_description,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select( q1_description,q5_registered,percentage)
q5q2

qry_w<-q5q2 %>% pivot_wider(names_from = q1_description, values_from = percentage)


knitr::kable(qry_w) %>% 
  kable_minimal()


```

___


**Register by subject or area**

+++++++REVISAR no esta OK el cruce+++

```{r q5_q4, echo=F, message=F, warning=F}

##AYE CORREGIR ESTO

q5q4<-base %>%
  group_by(q5_registered) %>%
  summarise(total=n(),
            fem=sum(q4_grouped_feminist==1),
            hr=sum(q4_grouped_hr==1),
            min=sum(q4_grouped_minorities==1),
            srhr=sum(q4_grouped_srhr==1),
        'Specific feminist subjects'=round(sum(q4_grouped_feminist==1)/total*100,2),
        'General HR Subjects'=round(sum(q4_grouped_hr==1)/total*100,2),
        'Intersectionality (minority groups)'=round(sum(q4_grouped_minorities==1)/total*100,2),
        'Sexual and reproductive health & rights'=round(sum(q4_grouped_srhr==1)/total*100,2))

q5q4<-arrange(q5q4, desc(q5_registered))

knitr::kable(q5q4) %>% 
  kable_minimal()

```
**--Analysis notes-----------------------------------------------------------------------**

It is more common to find unregistered feminist organizations than those that address gender issues through specific projects. It is necessary to verify whether this trend continues 

**------------------------------------------------------------------------------------------------**

___

**Scope:**

Q6. What is the geographical scope of your work?

```{r scope, echo=F, message=F, warning=F}

q6<-base %>% 
  group_by(q6_geo_scope) %>% 
  mutate(q6_geo_scope=forcats::fct_recode(as_factor(q6_geo_scope),
                                                     "Locally" = "locally_focused",
                                            "Nationally" = "nationally_focused",
                                          "Work from diaspora, refuge and/or exile" = "diaspora_and_or_exile",
                                          "Regionally" = "regionally_focused",
                                          "Transnationally" = "transnationally_focused",
                                          "Global" = "globally_focused")) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(q6_geo_scope) %>% 
  rename("Geo scope"=q6_geo_scope)


knitr::kable(q6) %>% 
  kable_minimal()
```
___

**Region:**

Q7. Indicate in which region(s) your group, organization and/or movement works

*Reading: 22% of the organizations work in South Asia.
Organizations working locally, regionally or globally were consolidated.*


```{r region, echo=F, message=F, warning=F}

q7_a<-base %>% 
  filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one) %>%
    mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%   summarise(n=n())%>% 
  rename(q7=q7_region_one) %>% 
  arrange(q7)

q7_select<-base %>% 
  select(starts_with("q7_region_multiple.")) %>% 
  filter(!is.na(q7_region_multiple.samerica))


q7_b<-q7_select%>% 
  summarize_all(sum) %>% 
  gather(q7, n) %>% 
  mutate(q7= str_replace(q7, "q7_region_multiple.", "")) %>% 
  mutate(q7=forcats::fct_recode(as_factor(q7),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica"))


q7_final <- q7_a %>% left_join(q7_b, by = "q7") %>% 
  mutate(n=n.x+n.y) %>% 
  select(-n.x,-n.y, "Region"=q7) %>%
  mutate(porcentaje=round((n/153)*100,1)) %>% 
  arrange(desc(porcentaje)) 
  


knitr::kable(q7_final) %>% 
  kable_minimal()

```
___

**Country:**

Q8. Which countries are you working in?

```{r country, include=F, echo=F, message=F, warning=F}

q8<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one, q8_country) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1))

q8<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one, q8_country) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1))


knitr::kable(q8) %>% 
  kable_minimal()
```
___

**Year of formation:**

Q9. What year was your group, organization and/ or movement formed?

*Reading: 36% of the respondent organizations were formed between the years 2015 and 2020, while around 13% were formed from the year 2021 onwards*
```{r year, echo=F, message=F, warning=F}
q9<-base %>% 
  mutate(q9_year_formation_agrup=case_when(
    q9_year_formation==2023 ~  1,
    q9_year_formation==2022 ~  2,
    q9_year_formation==2021 ~  3,
    q9_year_formation<2021 & q9_year_formation>2014 ~  4,
    q9_year_formation<2015 & q9_year_formation>2009 ~  5,
    q9_year_formation<2010 & q9_year_formation>1999 ~  6,
    is.na(q9_year_formation) ~ NA,
    TRUE ~  7)) %>%
  mutate(q9_year_formation_agrup=forcats::fct_recode(as_factor(q9_year_formation_agrup),
                                                     "Año 2023" = "1",
                                                     "Año 2022" = "2",
                                                     "Año 2021" = "3",
                                                     "Entre 2015 y 2020" = "4",
                                                     "Entre 2010 y 2014" = "5",
                                                     "Entre 2000 y 2009" = "6",
                                                     "Antes del 2000" = "7")) %>% 
  filter(!is.na(q9_year_formation_agrup)) %>% 
  group_by(q9_year_formation_agrup) %>% 
  summarise(total=n()) %>% 
  mutate(porcentaje=round((total/sum(total))*100,1)) %>% 
  arrange(q9_year_formation_agrup) %>% 
  rename("Year formation"=q9_year_formation_agrup)


knitr::kable(q9) %>% 
  kable_minimal()
```
___

**External founding:**

Q13. Between 2021 and 2023, has your group, organization and/or movement received any external funding?


```{r ef, echo=F, message=F, warning=F}
q13<-base %>%
  group_by(q13_ext_funding) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  rename("External funding"=q13_ext_funding)
 

knitr::kable(q13) %>% 
  kable_minimal()
```
___

**Language:**

Q46. In which language did you answer the survey?

```{r language, echo=F, message=F, warning=F}

q46<-base %>% 
  mutate(q46_language=case_when(
    q46_language=="english" ~ "English",
    q46_language=="spanish" ~ "Spanish",
    q46_language=="french" ~ "French",
    q46_language=="portuguese" ~ "Portuguese",
    q46_language=="arabic" ~ "Arabic",
    q46_language=="russian" ~ "Russian",
    TRUE ~ NA)) %>% 
  group_by(q46_language) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(q46_language) %>% 
  rename("Language"=q46_language)


knitr::kable(q46) %>% 
  kable_minimal()

```

___

##Previous WITM:

Q45. Did anyone from your group, organization and/or movement respond to AWID’s Where is the Money survey in 2008 or 2011?

```{r previous, echo=F, message=F, warning=F}


q45<-base %>%
  group_by(q45_previous_response) %>% 
  mutate(q45_previous_response=forcats::fct_recode(as_factor(q45_previous_response),
                                                     "Yes" = "yes",
                                            "No" = "no",
                                            "Don't know" = "99")) %>% 
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q45_previous_response)) %>% 
  rename("Previous response"=q45_previous_response)


knitr::kable(q45) %>% 
  kable_minimal()
```

