---
title: "WITM"
date: "`r Sys.Date()`"
output: html_document
---

#WITM Analysis - section 1 - v2

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, echo=F, message=F, warning=F}

#Library upload

library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(writexl)
library(eph)
library(openxlsx)
library(rmarkdown)
library(knitr)
library(kableExtra)

library(readr)
library(xlsx)

rm(list = ls())

```

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

This report filters only people who answered Q0=yes (i.e. who agree to answer the survey) and does not filter on question q1.

```{r upload, echo=T, message=F, warning=F}

# OPEN CSV file
witm <- read.csv2("Data/WITM_csv_last.csv")

source(file="WITM_variables.R") 

print(date())
```
___



**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Number of answers by date** 


```{r}
answers_by_date<-witm  %>% 
  group_by(date) %>%  
  summarise(qt=n())


ggplot(answers_by_date, aes(x =  as.POSIXct(date), y=qt)) +                      
  geom_bar(stat="identity",width=0.5, colour="red", fill="skyblue") +
  labs(x="date",y= "Number") +                 
  ggtitle("Number of answers by date") +                
  theme_bw(base_size = 12)+  
  scale_x_datetime(breaks=scales::breaks_pretty(8))+
  geom_text(aes(label = signif(qt)), nudge_y = 3)
```


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Group information:**

Q2. Which of the following statements best describes your group, organization and/or movement?

```{r info, echo=F, message=F, warning=F}
q1<-base %>%
  group_by(q1_description) %>% 
  mutate(q1_description=forcats::fct_recode(as_factor(q1_description),
                                                     "We promote the rights of women or girls or trans or gender diverse people in all their intersecting identities and this is the 'primary focus of all our work'" = "primary_focus",
                                            "We promote the rights of women or girls or trans or gender diverse people with intersecting identities 'through specific project(s)', but not as the primary focus of our work" = "specific_projects",
                                            "Other" = "98")) %>%
  summarise(n=n()) %>% 
  mutate(porcentaje=round((n/sum(n))*100,1)) %>% 
  arrange(desc(q1_description)) %>% 
  rename("Description"=q1_description)


knitr::kable(q1) %>% 
  kable_minimal()
```


___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Organization names:**

Q3. The name of your group, organization and/or movement


```{r name1, echo=F, message=F, warning=F}

n_temp<-sum(base$q2_name=="")
print(paste("The number of organisations that did not answer their name is:",n_temp))


```
**--Analysis notes-----------------------------------------------------------------------**

Very interesting that almost all organisations responded with their name despite the fact that the possibility of not responding is informed and underlined.

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Type of organization**

Q4. Which of the following forms of organizing best describes your group, organization and/or movement?

*This is a multiple-choice question so the sum of the % does NOT add up to 100.*

```{r type, echo=F, message=F, warning=F}

#Total valid responses for calculating percentage

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(starts_with("q4_forms_organizing."))
#q4_select

#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Black rights/ Black feminist rights"="q4_forms_organizing.black_rights",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Crisis response"="q4_forms_organizing.crisis_response",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                "Digital rights"="q4_forms_organizing.digital_rights",
                                "Disability rights and justice"="q4_forms_organizing.disability_rights",
                                "Displaced, migrant and refugee rights"="q4_forms_organizing.displaced_migrant_refugee_rights",
                                "Economic justice, rights and alternatives"="q4_forms_organizing.economic_justice",
                                "Freedom of information and media"="q4_forms_organizing.information_media_freedom",
                                "Harm reduction"="q4_forms_organizing.harm_reduction",
                                "Ending gender based violence"="q4_forms_organizing.end_gender_violence",
                                "Pleasure and bodily care"="q4_forms_organizing.pleasure_bodily_care",
                                "Resisting the war on drugs"="q4_forms_organizing.resisting_war_on_drugs",
                                "Rights for people living with HIV+"="q4_forms_organizing.rights_for_people_living_with_hiv",
                                "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Human rights"="q4_forms_organizing.human_rights",
                                "Indigenous rights"="q4_forms_organizing.indigenous_rights",
                                "Intersex rights"="q4_forms_organizing.intersex_rights",
                                "Labour rights"="q4_forms_organizing.labour_rights",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Racial justice"="q4_forms_organizing.racial_justice",
                                "Religious and ethnic minority rights"="q4_forms_organizing.religious_ethnic_minority_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Sexual and reproductive health & rights (SRHR) and bodily autonomy"="q4_forms_organizing.srhr_bodily_autonomy",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Women's rights"="q4_forms_organizing.womens_rights",
                                "Young feminists"="q4_forms_organizing.young_feminists",
                                "Girls’ movements"="q4_forms_organizing.girls_movements",
                                "Human rights defenders at risk"="q4_forms_organizing.hr_defenders_at_risk",
                                "Other"="q4_forms_organizing.98"))%>% 
  mutate(porcentaje=round(n/total*100,1)) %>% 
  arrange(desc(porcentaje)) %>% 
  rename("Organization type"=q4)

#write.xlsx2(as.data.frame(q4), "Output/section1.xlsx", row.names = FALSE, sheetName ="q4",append = TRUE)




knitr::kable(q4) %>% 
  kable_minimal()

```

___


**Type of organization - grouped (q4_grouped)**

This variable is constructed by recognizing the organizations that work on one of AWID's focus topics and those that do not, are placed as "other subjects (not focus)".

-	Lesbian, bisexual and queer rights 
-	Sex workers rights
-	Trans and non-binary-rights
-	Anti-caste 
-	Climate and environmental justice  
-	Countering anti-gender and anti-rights 
-	Anti-militarization and peace 
-	Holistic safety, protection and collective care 



```{r type_grouped, echo=F, message=F, warning=F}
q4_focus<-base %>%
  filter( q4_grouped_feminist!="98") %>%
  group_by(q4_awid_focus) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  mutate(q4_awid_focus=recode(q4_awid_focus,"1"="Specific AWID subjects","0"="Other subjects")
         )


knitr::kable(q4_focus) %>% 
  kable_minimal()

```
___

```{r}

total<-base %>%
  count(q4_forms_organizing) %>% 
  summarise(n=sum(n))

total<-total$n

#lo pase a variables
# base<- base %>%
#   mutate(q4_awid_focus_no=case_when
#          (q4_awid_focus!=1 ~ 1, TRUE ~0))  
  

#Choose only multiple-choice answers -Q4-
q4_select<-base %>% 
  select(q4_forms_organizing.lesbian_bisexual_queer_rights,
            q4_forms_organizing.sex_workers_rights,
            q4_forms_organizing.trans_non_binary_rights,
            q4_forms_organizing.anti_caste,
            q4_forms_organizing.climate_justice,
            q4_forms_organizing.countering_anti_gender,
            q4_forms_organizing.anti_militarization,
            q4_forms_organizing.holistic_safety_protection_collective_care,
            q4_awid_focus_no
         )
#q4_select


#q4 calculation
q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"
                   ))%>% 
  mutate(Percentage=round(n/total*100,1)) %>% 
  arrange(desc(Percentage)) %>% 
  rename("Organization type"=q4)


knitr::kable(q4) %>% 
  kable_minimal()




```

```{r}

q4<-q4_select%>% 
  summarize_all(sum) %>% 
  gather(q4, n) %>%
  mutate(q4=forcats::fct_recode(as_factor(q4),
                                "Anti-caste"="q4_forms_organizing.anti_caste",
                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"
                   ))%>% 
  mutate(Percentage=round(n/total*100,1)) %>% 
  arrange(desc(Percentage)) 


ggplot(q4, aes(x = q4, y = Percentage, fill = q4)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), hjust = -0.1, size = 3.5) +
  labs(title = "Subjects grouped",
       x = "Subjects",
       y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "none")+
   coord_flip()

```


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Register**

Q5. Is your group, organization and/or movement registered?

```{r registered, echo=F, message=F, warning=F}

q5<-base %>%
  group_by(q5_registered) %>% 
  mutate(q5_registered= case_when(
    q5_registered=="y_registered" ~ "Yes",
    q5_registered=="n_registered" ~ "No",
    q5_registered==98 ~ "Other",
    TRUE ~ NA)) %>%  
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1)) %>% 
  arrange(desc(n)) %>% 
  rename("Register"=q5_registered)

knitr::kable(q5) %>% 
  kable_minimal()

```
```{r}

q5 <- q5 %>% filter(!is.na(Register))

ggplot(q5, aes(x = Register, y = Percentage, fill = Register)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5, size = 3.5) +
  labs(title = "Registered",
       x = "Scope",
       y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "none")

```

___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope:**

Q6. What is the geographical scope of your work?

```{r scope, echo=F, message=F, warning=F}

q6<-base %>% 
  group_by(q6_geo_scope) %>% 
  mutate(q6_geo_scope=forcats::fct_recode(as_factor(q6_geo_scope),
                                          "Locally" = "locally_focused",
                                          "Nationally" = "nationally_focused",
                                          "Diaspora" = "diaspora_and_or_exile",
                                          "Regionally" = "regionally_focused",
                                          "Transnationally" = "transnationally_focused",
                                          "Global" = "globally_focused")) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage = n/sum(n) * 100)  %>% 
  arrange(desc(Percentage)) 



knitr::kable(q6) %>% 
  kable_minimal()
```

```{r}

ggplot(q6, aes(x = q6_geo_scope, y = Percentage, fill = q6_geo_scope)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5, size = 3.5) +
  labs(title = "Geographical scope",
       x = "Scope",
       y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "none")

```


**Region:**

Q7. Indicate in which region(s) your group, organization and/or movement works

*Reading: 22% of the organizations work in South Asia.
Organizations working locally, regionally or globally were consolidated.*


```{r region, echo=F, message=F, warning=F}



q7_a<-base %>% 
  filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one) %>%
    mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%   summarise(n=n())%>% 
  rename(q7=q7_region_one) %>% 
  arrange(q7)

q7_select<-base %>% 
  select(starts_with("q7_region_multiple.")) %>% 
  filter(!is.na(q7_region_multiple.samerica))


q7_b<-q7_select%>% 
  summarize_all(sum) %>% 
  gather(q7, n) %>% 
  mutate(q7= str_replace(q7, "q7_region_multiple.", "")) %>% 
  mutate(q7=forcats::fct_recode(as_factor(q7),
                                 "South America" = "samerica",
                                 "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica"))


q7_final <- q7_a %>% left_join(q7_b, by = "q7") %>% 
  mutate(n=n.x+n.y) %>% 
  select(-n.x,-n.y, "Region"=q7) %>%
  mutate(porcentaje=round((n/153)*100,1)) %>% 
  arrange(desc(porcentaje)) 
  
knitr::kable(q7_final) %>% 
  kable_minimal()

```


___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Country:**

Q8. Which countries are you working in?



```{r q6, recho=F, message=F, warning=F}

#Convertir campos vacíos de la variable country en NA
 base <- base %>%
  mutate(q8_country = na_if(q8_country, ""))

base<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                                     "South America" = "samerica",
                                            "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%
  mutate(q8_country=forcats::fct_recode(as_factor(q8_country),
                                      "Afghanistan"="afghanistan",
                                      "Albania"="albania",
                                      "Algeria"="algeria",
                                      "American Samoa"="american_samoa",
                                      "Andorra"="andorra",
                                      "Angola"="angola",
                                      "Anguilla"="anguilla",
                                      "Antigua and Barbuda"="antigua_and_barbuda",
                                      "Argentina"="argentina",
                                      "Armenia"="armenia",
                                      "Aruba"="aruba",
                                      "Australia"="australia",
                                      "Austria"="austria",
                                      "Azerbaijan"="azerbaijan",
                                      "Bahamas"="bahamas",
                                      "Bahrain"="bahrain",
                                      "Bangladesh"="bangladesh",
                                      "Barbados"="barbados",
                                      "Belarus"="belarus",
                                      "Belgium"="belgium",
                                      "Belize"="belize",
                                      "Benin"="benin",
                                      "Bhutan"="bhutan",
                                      "Bolivia"="bolivia",
                                      "Bonaire, Sint Eustatius and Saba"="bonaire_sint_eustatius_saba",
                                      "Bosnia and Herzegovina"="bosnia_and_herzegovina",
                                      "Botswana"="botswana",
                                      "Brazil"="brazil",
                                      "British Virgin Islands"="british_virgin_islands",
                                      "Brunei Darussalam"="brunei_darussalam",
                                      "Bulgaria"="bulgaria",
                                      "Burkina Faso"="burkina_faso",
                                      "Burundi"="burundi",
                                      "Cabo Verde"="cabo_verde",
                                      "Cambodia"="cambodia",
                                      "Cameroon"="cameroon",
                                      "Canada"="canada",
                                      "Cayman Islands"="cayman_islands",
                                      "Central African Republic"="cafrican_republic",
                                      "Chad"="chad",
                                      "Chile"="chile",
                                      "China"="china",
                                      "Colombia"="colombia",
                                      "Comoros"="comoros",
                                      "Congo"="congo",
                                      "Cook Islands"="cook_islands",
                                      "Costa Rica"="costa_rica",
                                      "Côte d'Ivoire"="côte_divoire",
                                      "Croatia"="croatia",
                                      "Cuba"="cuba",
                                      "Curaçao"="curaçao",
                                      "Cyprus"="cyprus",
                                      "Czech Republic"="czech_republic",
                                      "Dem. People's Republic of Korea"="dem_peoples_rep_of_korea",
                                      "Democratic Republic of the Congo"="democratic_republic_of_the_congo",
                                      "Denmark"="denmark",
                                      "Djibouti"="djibouti",
                                      "Dominica"="dominica",
                                      "Dominican Republic"="dominican_republic",
                                      "Ecuador"="ecuador",
                                      "Egypt"="egypt",
                                      "El Salvador"="el_salvador",
                                      "Equatorial Guinea"="equatorial_guinea",
                                      "Eritrea"="eritrea",
                                      "Estonia"="estonia",
                                      "Eswatini"="eswatini",
                                      "Ethiopia"="ethiopia",
                                      "Fiji"="fiji",
                                      "Finland"="finland",
                                      "France"="france",
                                      "French Guiana"="french_guiana",
                                      "French Polynesia"="french_polynesia",
                                      "Gabon"="gabon",
                                      "Gambia"="gambia",
                                      "Georgia"="georgia",
                                      "Germany"="germany",
                                      "Ghana"="ghana",
                                      "Greece"="greece",
                                      "Greenland"="greenland",
                                      "Grenada"="grenada",
                                      "Guadeloupe"="guadeloupe",
                                      "Guam"="guam",
                                      "Guatemala"="guatemala",
                                      "Guinea"="guinea",
                                  "Guinea-Bissau"="guinea_bissau",
                                      "Guyana"="guyana",
                                      "Haiti"="haiti",
                                      "Honduras"="honduras",
                                      "Hong Kong"="hong_kong",
                                      "Hungary"="hungary",
                                      "Iceland"="iceland",
                                      "India"="india",
                                      "Indonesia"="indonesia",
                                      "Iran"="iran",
                                      "Iraq"="iraq",
                                      "Ireland"="ireland",
                                      "Israel"="israel",
                                      "Italy"="italy",
                                      "Jamaica"="jamaica",
                                      "Japan"="japan",
                                      "Jordan"="jordan",  
                                      "Kazakhstan"="kazakhstan",
                                  "Kenya"="kenya",
                                  "Kiribati"="kiribati",
                                  "Kuwait"="kuwait",
                                  "Kyrgyzstan"="kyrgyzstan",
                                  "Lao People's Democratic Republic"="lao_peoples_democratic_republic",
                                  "Latvia"="latvia",
                                  "Lebanon"="lebanon",
                                  "Lesotho"="lesotho",
                                  "Liberia"="liberia",
                                  "Libya"="libya",
                                  "Liechtenstein"="liechtenstein",
                                  "Lithuania"="lithuania",
                                  "Luxembourg"="luxembourg",
                                  "Macao"="macao",
                                  "Madagascar"="madagascar",
                                  "Malawi"="malawi",
                                  "Malaysia"="malaysia",
                                  "Maldives"="maldives",
                                  "Mali"="mali",
                                  "Malta"="malta",
                                  "Marshall
                                  Islands"="marshall_islands",
                                  "Martinique"="martinique",
                                  "Mauritania"="mauritania",
                                  "Mauritius"="mauritius",
                                  "Mayotte"="mayotte",
                                  "Mexico"="mexico",
                                  "Micronesia (Fed. States of)"="micronesia_fed_states_of",
                                  "Monaco"="monaco",
                                  "Mongolia"="mongolia",
                                  "Montenegro"="montenegro",
                                  "Montserrat"="montserrat",
                                  "Morocco"="morocco",
                                  "Mozambique"="mozambique",
                                  "Myanmar"="myanmar",
                                  "Namibia"="namibia",
                                  "Nauru"="nauru",
                                  "Nepal"="nepal",
                                  "Netherlands"="netherlands",
                                  "New Caledonia"="new_caledonia",
                                  "New Zealand"="new_zealand",
                                  "Nicaragua"="nicaragua",
                                  "Niger"="niger",
                                  "Nigeria"="nigeria",
                                "Niue"="niue",
                                "North Macedonia"="north_macedonia",
                                "Northern Mariana Islands"="northern_mariana_islands",
                                "Norway"="norway",
                                "Oman"="oman",
                                "Pakistan"="pakistan",
                                "Palau"="palau",
                                "Palestine"="palestine",
                                "Panama"="panama",
                                "Papua New Guinea"="papua_new_guinea",
                                "Paraguay"="paraguay",
                                "Peru"="peru",
                                "Philippines"="philippines",
                                "Poland"="poland",
                                "Portugal"="portugal",
                                "Puerto Rico"="puerto_rico",
                                "Qatar"="qatar",
                                "Republic of Korea"="republic_of_korea",
                                "Republic of Moldova"="republic_of_moldova",
                                "Réunion"="reunion",
                                "Romania"="romania",
                                "Russia"="russia",
                                "Rwanda"="rwanda",
                                "Saint Barthélemy"="saint_barthelemy",
                                "Saint Helena"="saint_helena",
                                "Saint Kitts and Nevis"="saint_kitts_and_nevis",
                                "Saint Lucia"="saint_lucia",
                                "Saint Martin (French part)"="saint_martin_french_part",
                                "Saint Vincent and the Grenadines"="saint_vincent_and_the_grenadines",
                                "Samoa"="samoa",
                                "San Marino"="san_marino",
                                "Sao Tome and Principe"="sao_tome_and_principe",
                                "Saudi Arabia"="saudi_arabia",
                                "Senegal"="senegal",
                                "Serbia"="serbia",
                                "Seychelles"="seychelles",
                                "Sierra Leone"="sierra_leone",
                                "Singapore"="singapore",
                                "Sint Maarten (Dutch part)"="sint_maarten_dutch_part",
                                "Slovakia"="slovakia",
                                "Slovenia"="slovenia",
                                "Solomon Islands"="solomon_islands",
                                "Somalia"="somalia",
                                "South Africa"="south_africa",
                                "South Sudan"="south_sudan",
                                "Spain"="spain",
                                "Sri Lanka"="sri_lanka",
                                "Sudan"="sudan",
                                "Suriname"="suriname",
                                "Sweden"="sweden",
                                "Switzerland"="switzerland",
                                "Syrian Arab Republic"="syrian_arab_republic",
                                "Taiwan"="taiwan",
                                "Tajikistan"="tajikistan",
                                "Tanzania"="tanzania",
                                "Thailand"="thailand",
                                "Timor-Leste"="timor_leste",
                                "Togo"="togo",
                                "Tokelau"="tokelau",
                                "Tonga"="tonga",
                                "Trinidad and Tobago"="trinidad_and_tobago",
                                "Tunisia"="tunisia",
                                "Turkey"="turkey",
                                "Turkmenistan"="turkmenistan",
                                "Turks and Caicos Islands"="turks_and_caicos_islands",
                                "Tuvalu"="tuvalu",
                                "Uganda"="uganda",
                                "Ukraine"="ukraine",
                                "United Arab Emirates"="united_arab_emirates",
                                "United Kingdom"="united_kingdom",
                                "United States of America"="united_states_of_america",
                                "Uruguay"="uruguay",
                                "Uzbekistan"="uzbekistan",
                                "Vanuatu"="vanuatu",
                                "Venezuela (Bolivarian Republic of)"="venezuela_bolivarian_republic_of",
                                "Viet Nam"="viet_nam",
                                "Wallis and Futuna Islands"="wallis_and_futuna_islands",
                                "Western Sahara"="western_sahara",
                                "Yemen"="yemen",
                                "Zambia"="zambia",
                                "Zimbabwe"="zimbabwe",
                                "Other South America"="country_other1",
                                "Other Central America & Mexico"="country_other2",
                                "Other North America"="country_other3",
                                "Other Caribbean"="country_other4",
                                "Other South Asia"="country_other5",
                                "Other Southeast Asia"="country_other6",
                                "Other East Asia"="country_other7",
                                "Other The Pacific"="country_other8",
                                "Other South West Asia/Middle East"="country_other9",
                                "Other Central Asia & Caucasus"="country_other10",
                                "Other Eastern Europe, Southeast Europe and Central Europe"="country_other11",
                                "Other Western Europe"="country_other13",

                              "Other West Africa"="country_other14",
                              "Other East Africa"="country_other15",
                              "Other Southern Africa"="country_other16",
                              "Other Central Africa"="country_other17",
                              "Other North Africa"="country_other18"))


q8<-base %>% 
  filter(q6_geo_scope=="locally_focused"| q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one, q8_country) %>% 
  summarise(n=n()) %>% 
  mutate(Percentage=round((n/sum(n))*100,1))

knitr::kable(q8) %>% 
  kable_minimal()

```




**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year of formation:**

Q9. What year was your group, organization and/ or movement formed?

*Reading: 36% of the respondent organizations were formed between the years 2015 and 2020, while around 13% were formed from the year 2021 onwards*


```{r year, echo=F, message=F, warning=F}


    

q9<-base %>% 
  filter(!is.na(q9_year_formation_agrup)) %>% 
  group_by(q9_year_formation_agrup) %>% 
  summarise(total=n()) %>% 
  mutate(Percentage=round((total/sum(total))*100,1)) %>% 
  arrange(q9_year_formation_agrup) 


knitr::kable(q9) %>% 
  kable_minimal()


```


```{r}

ggplot(q9, aes(x = q9_year_formation_agrup, y = Percentage, fill = q9_year_formation_agrup)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5, size = 3.5) +
  labs(title = "Year of formation",
       x = "Year",
       y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "none")

```





**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

##CROSSTABS 


**AWID FOCUS SUBJECTS BY REGISTRATION**


A crosstabulation (bivariate) of the combination of registration and subject of the organisation 


```{r}


 # "Anti-caste"="q4_forms_organizing.anti_caste",
 #                                "Anti-militarization and peace"="q4_forms_organizing.anti_militarization",
 #                                "Climate and environmental justice"="q4_forms_organizing.climate_justice",
 #                                "Countering anti-gender and anti-rights"="q4_forms_organizing.countering_anti_gender",
 #                                 "Holistic safety, protection and collective care"="q4_forms_organizing.holistic_safety_protection_collective_care",
 #                                "Lesbian, Bisexual and queer rights"="q4_forms_organizing.lesbian_bisexual_queer_rights",
 #                                "Sex workers rights"="q4_forms_organizing.sex_workers_rights",
 #                                "Trans and non-binary rights"="q4_forms_organizing.trans_non_binary_rights",
 #                                "Other feminists subjects (not AWID focus)"="q4_awid_focus_no"


## Anti-caste 
q5q4_anti_caste<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.anti_caste,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.anti_caste,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q5q4_peace<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.anti_militarization,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.anti_militarization,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q5q4_climate<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.climate_justice,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.climate_justice,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q5q4_anti_rights<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.countering_anti_gender,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.countering_anti_gender,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q5q4_care<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.holistic_safety_protection_collective_care,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q5q4_lesbian<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.lesbian_bisexual_queer_rights,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q5q4_sex_workers<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.sex_workers_rights,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.sex_workers_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q5q4_trans<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_forms_organizing.trans_non_binary_rights,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_forms_organizing.trans_non_binary_rights,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q5q4_others<-base %>%
  filter(!is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>%
  group_by(q4_awid_focus_no,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q5_registered,q4_grouped=q4_awid_focus_no,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )

q5q4_all<-bind_rows(q5q4_anti_caste,q5q4_peace,q5q4_climate,q5q4_anti_rights,q5q4_care,q5q4_lesbian,q5q4_sex_workers,q5q4_trans,q5q4_others)

q5q4_all <-q5q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q5_registered,percentage)

#q5q4_all
qry_w<-q5q4_all %>% pivot_wider(names_from = q5_registered, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```



```{r}
#q5q4_all

#qry_graph

ggplot(q5q4_all, aes(x = q4_grouped, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Subject grouped by registration (%)") +                
  theme_minimal() +
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) +
  #geom_text(aes(label = sprintf("%.1f%%", percentage)), hjust = -0.1, size = 3.5) +
   coord_flip()


```


**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**


**SUBJECTS GROUPED BY SCOPE**

Percentage

```{r}
#!is.na(q6_geo_scope) & q6_geo_scope!=""

## Anti-caste 
q6q4_anti_caste<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.anti_caste)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.anti_caste,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q6q4_peace<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.anti_militarization)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.anti_militarization,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q6q4_climate<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.climate_justice)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.climate_justice,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q6q4_anti_rights<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.countering_anti_gender)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.countering_anti_gender,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q6q4_care<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.holistic_safety_protection_collective_care)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q6q4_lesbian<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.lesbian_bisexual_queer_rights)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q6q4_sex_workers<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.sex_workers_rights)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.sex_workers_rights,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q6q4_trans<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_forms_organizing.trans_non_binary_rights)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_forms_organizing.trans_non_binary_rights,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q6q4_others<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope,q4_awid_focus_no)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q6_geo_scope,q4_grouped=q4_awid_focus_no,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )
q6q4_total<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="98" & q6_geo_scope!="") %>%
  group_by(q6_geo_scope)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q4_grouped="total")%>%
  select(q6_geo_scope,q4_grouped,n,percentage)
 
         
q6q4_all<-bind_rows(q6q4_anti_caste,q6q4_peace,q6q4_climate,q6q4_anti_rights,q6q4_care,q6q4_lesbian,q6q4_sex_workers,q6q4_trans,q6q4_others,q6q4_total)

q6q4_all <-q6q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q6_geo_scope,percentage)

#q5q4_all
qry_w<-q6q4_all %>% pivot_wider(names_from = q6_geo_scope, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```


**--LECTURE-----------------------------------------------------------------------**


Among the Nationally focused 3.2% indicated working on anti-caste issues.

**-----------------------------------------------------------------------------------------**



**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**SUBJECTS GROUPED BY SCOPE**

Absoluts numbers

```{r}

q6q4_all<-bind_rows(q6q4_anti_caste,q6q4_peace,q6q4_climate,q6q4_anti_rights,q6q4_care,q6q4_lesbian,q6q4_sex_workers,q6q4_trans,q6q4_others,q6q4_total)
q6q4_all <-q6q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q6_geo_scope,n)

#q5q4_all
qry_w<-q6q4_all %>% pivot_wider(names_from = q6_geo_scope, values_from = n) 

knitr::kable(qry_w) %>% 
  kable_minimal()
```




**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**SUBJECTS GROUPED BY SCOPE (NATIONAL AND LOCAL)**



```{r}
#q5q4_all

q6q4_all<-bind_rows(q6q4_anti_caste,q6q4_peace,q6q4_climate,q6q4_anti_rights,q6q4_care,q6q4_lesbian,q6q4_sex_workers,q6q4_trans,q6q4_others,q6q4_total)
q6q4_all <-q6q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q6_geo_scope,percentage)

qry_graph<-q6q4_all %>% filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused")


ggplot(qry_graph, aes(x = q4_grouped, y=percentage, fill=q6_geo_scope)) +                      
   geom_bar(position="dodge", stat="identity") +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Subject grouped by registration (%)") +                
  theme_minimal() +
  geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) +
  #geom_text(aes(label = sprintf("%.1f%%", percentage)), hjust = -0.1, size = 3.5) +
   coord_flip()


```



**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**SUBJECTS GROUPED BY YEAR OF FORMATION**


Percentage

```{r}

##delte variables to clean environment
rm(list=setdiff(ls(), "base"))

#q9_year_formation_agrup

## Anti-caste 
q9q4_anti_caste<-base %>%
  filter(!is.na(q9_year_formation_agrup)  & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.anti_caste,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.anti_caste,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti Caste","0"="Other subjects")
         )

## Anti-militarization and peace
q9q4_peace<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.anti_militarization,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.anti_militarization,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Anti-militarization and peace","0"="Other subjects")
         )

## Climate and environmental justice 
q9q4_climate<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.climate_justice,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.climate_justice,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Climate and environmental justice","0"="Other subjects")
         )

## Countering anti-gender and anti-rights
q9q4_anti_rights<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.countering_anti_gender,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.countering_anti_gender,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Countering anti-gender and anti-rights","0"="Other subjects")
         )


## Holistic safety, protection and collective care
q9q4_care<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.holistic_safety_protection_collective_care,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.holistic_safety_protection_collective_care,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Holistic safety, protection and collective care","0"="Other subjects")
         )

## Lesbian, Bisexual and queer rights
q9q4_lesbian<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.lesbian_bisexual_queer_rights,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.lesbian_bisexual_queer_rights,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Lesbian, Bisexual and queer rights","0"="Other subjects")
         )

## Sex workers rights
q9q4_sex_workers<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.sex_workers_rights,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.sex_workers_rights,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Sex workers rights","0"="Other subjects")
         )


##Trans and non-binary rights
q9q4_trans<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_forms_organizing.trans_non_binary_rights,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_forms_organizing.trans_non_binary_rights,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Trans and non-binary rights","0"="Other subjects")
         )

##Other feminists subjects (not AWID focus)
q9q4_others<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q4_awid_focus_no,q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  select(q9_year_formation_agrup,q4_grouped=q4_awid_focus_no,n,percentage) %>%
  mutate(q4_grouped=recode(q4_grouped,"1"="Other feminists subjects (not AWID focus)","0"="Other subjects")
         )
q9q4_total<-base %>%
  filter(!is.na(q9_year_formation_agrup) & q9_year_formation_agrup!="98" & q9_year_formation_agrup!="") %>%
  group_by(q9_year_formation_agrup)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q4_grouped="total")%>%
  select(q9_year_formation_agrup,q4_grouped,n,percentage)
 
         
q9q4_all<-bind_rows(q9q4_anti_caste,q9q4_peace,q9q4_climate,q9q4_anti_rights,q9q4_care,q9q4_lesbian,q9q4_sex_workers,q9q4_trans,q9q4_others,q9q4_total)

q9q4_all <-q9q4_all %>% filter(q4_grouped!="Other subjects") %>% select(q4_grouped,q9_year_formation_agrup,percentage) %>% arrange(q9_year_formation_agrup)

#q5q4_all
qry_w<-q9q4_all %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage) 

knitr::kable(qry_w) %>% 
  kable_minimal()



```


**--LECTURE-----------------------------------------------------------------------**


70% of organizations working on anti-caste issues started after 2020.

**-----------------------------------------------------------------------------------------**



**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Scope by registration**


A crosstabulation (bivariate) of the combination of registered and scope

```{r}

##borrar las variables para evitar problemas
#rm(list=setdiff(ls(), "base"))

q6q5<-base %>%
  filter(!is.na(q6_geo_scope) & q6_geo_scope!="" & !is.na(q5_registered) & q5_registered!="") %>%
  group_by(q6_geo_scope,q5_registered)%>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q6_geo_scope=recode(q6_geo_scope,
          "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Diaspora",
         "regionally_focused"= "Regionally",
          "transnationally_focused"="Transnationally",
         "globally_focused"="Global"
         ) ) %>%
  select(q5_registered,Scope=q6_geo_scope,percentage)

#q6q5
qry_w<-q6q5 %>% pivot_wider(names_from = Scope, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))

knitr::kable(qry_w) %>% 
  kable_minimal()


```

```{r}
#q5q2

qry_graph<-q6q5 %>% filter((q5_registered=="y_registered" | q5_registered=="n_registered") )
                      #& (Scope=="Nationally"  | Scope=="Locally" | Scope=="Regionally"))
#qry_graph

ggplot(qry_graph, aes(x = Scope, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Subjects",y= "%") +                 
  ggtitle("Registration by Geographic scope (%)") +                
  theme_light()+
 geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) +
   coord_flip()

```
**--Lecture -----------------------------------------------------------------------**

19.7% of the local organizations are not registered

**------------------------------------------------------------------------------------------------**




**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Region by register**

This is made now only for Locally and National organisations

```{r region_q5, echo=F, message=F, warning=F}

rm(list=setdiff(ls(), "base"))

q5q7<-base %>% 
  filter(q6_geo_scope=="locally_focused" | q6_geo_scope=="nationally_focused") %>% 
  group_by(q7_region_one,q5_registered) %>%
  summarise(n=n()) %>%
  mutate(percentage=round((n/sum(n))*100,1))%>%
  arrange(desc(n)) %>% 
  mutate(q7_region_one=forcats::fct_recode(as_factor(q7_region_one),
                                    "South America" = "samerica",
                                    "Central America & Mexico" = "camerica",
                                    "North America" = "namerica",
                                    "Caribbean" = "caribbean",
                                    "South Asia" = "sasia",
                                    "Southeast Asia" = "seasia",
                                    "East Asia" = "easia",
                                    "The Pacific" = "pacific",
                                    "South West Asia/Middle East" = "swasiamiddleeast",
                                    "Central Asia & Caucasus" = "casia",
                                    "Eastern Europe, Southeast Europe and Central Europe" = "caucasuseurope",
                                    "Western Europe" = "weurope",
                                    "West Africa"="wafrica",
                                    "East Africa"="eafrica",
                                    "Southern Africa"="safrica",
                                    "Central Africa"="cafrica",
                                    "North Africa"="nafrica")) %>%
  select(q5_registered,Region=q7_region_one,percentage)

qry_w<-q5q7 %>% pivot_wider(names_from = Region, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))


knitr::kable(t(qry_w)) %>% 
  kable_minimal()

```

**--Analysis notes-----------------------------------------------------------------------**

Between local and national organizations there is a big difference in how many are unregistered in the different regions. The region with the highest proportion of unregistered is North Africa followed by North America.

**------------------------------------------------------------------------------------------------**


___

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year of formation & Register**



```{r year_register, echo=F, message=F, warning=F}



q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup) & !is.na(q5_registered) & q5_registered!="98" & q5_registered!="") %>% 
  group_by(q9_year_formation_agrup,q5_registered) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  select(q9_year_formation_agrup,q5_registered,percentage)


qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage) %>%
 mutate(q5_registered=recode(q5_registered, "98"="Other", "n_registered"="No registered", "y_registered"="Registered"))


knitr::kable(qry_w) %>% 
  kable_minimal()



```


```{r}
#q8

  qry_graph<-q8 %>% filter((q5_registered=="y_registered" | q5_registered=="n_registered"))
#qry_graph

ggplot(qry_graph, aes(x = q9_year_formation_agrup, y=percentage, fill=q5_registered)) +                      
   geom_bar(position="dodge", stat="identity") +
  scale_colour_distiller() +
  labs(x="Year",y= "%") +                 
  ggtitle("Year of statup by Registration (%)") +                
  theme_light()+
 geom_text(aes(label = sprintf("%0.1f", round(percentage, digits = 1))),position=position_dodge(width=0.9),
            vjust=0.5, hjust=1,size=3) +
   coord_flip()


```



**--Lecture----------------------------------------------------------------------**

Organizations starting in the last 3 years have a high proportion of non-registration. It decreases as the start-up time passes.


**------------------------------------------------------------------------------------------------**

**-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-**

**Year by Gegraphically Scope**



```{r year_q6, echo=F, message=F, warning=F}

#rm(list=setdiff(ls(), "base"))

qry<-base %>%
    group_by(q6_geo_scope) %>%
  summarise(n=n())

qry

q8<-base %>% 
  filter(!is.na(q9_year_formation_agrup) & !is.na(q6_geo_scope)) %>% 
  group_by(q6_geo_scope,q9_year_formation_agrup) %>% 
  summarise(n=n()) %>% 
  mutate(percentage=round((n/sum(n))*100,1)) %>%
  mutate(q6_geo_scope=recode(q6_geo_scope,
     "locally_focused"="Locally",
         "nationally_focused"="Nationally" ,
         "diaspora_and_or_exile"="Work from diaspora, refuge and/or exile",
         "regionally_focused"= "Regionally",
         "transnationally_focused"="Transnationally",
         "globally_focused"="Global")) %>%
  select(q9_year_formation_agrup,q6_geo_scope,percentage)


qry_w<-q8 %>% pivot_wider(names_from = q9_year_formation_agrup, values_from = percentage)
       
 


knitr::kable(qry_w) %>% 
  kable_minimal()



```






